---
title: "kats simple QB"
author: "Kat Leigh"
date: "11/24/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

# Packages
library(tidyverse)
library(Matrix)
library(kableExtra)
library(ggplot2)
library(plotly)
library(lpSolve)
library(lpSolveAPI)
```

```{r}
source("stock_dynamic.R")
source("harvest_species.R")
source("harvest_tech.R")
source("profit_tech.R")
source("pvnb.R")
```


```{r} 
# First, set seed to ensure we have the same result 
set.seed(666)


# set the number of species and technologies we want to study
species_num <- 2
tech_num <- 2


# set the number of years we want to model the stock dynamic 
year = 5

# set the discount rate
delta = 0.05
rho = 1/(1+delta)


# set values for variables in the "Our Model" section
# set parameters
species <- c(1:species_num)
parameter <- data.frame(1:6)
parameter$r <- c(seq(0,1,0.2))
parameter$K <- c(seq(0,5,1))
parameter$X0 <- c(seq(0,1,0.2))
parameter$p <- c(seq(0,200,34))
parameter$c <- c(seq(0,100,19))
parameter$delta <- c(seq(0,0.05,0.01))
parameter$rho <- 1/(1+parameter$delta)

# set catchability coefficient (q)
q <- c(seq(0,1,0.2) )

# set effort
E <- c(seq(0,1,0.2))


r_array <- array(c(seq(0,1,1/(species_num-1))), c(species_num, year)) 
K_array <- array(c(seq(0,5,5/(species_num-1))), c(species_num, year))

parameter$X0 <- c(seq(0,1,1/(species_num-1)))
parameter$p <- c(seq(0,200,200/(species_num-1)))
parameter$c <- c(seq(0,100,100/(species_num-1)))
parameter$delta <- c(seq(0,0.05,0.05/(species_num-1)))
parameter$rho <- 1/(1+parameter$delta)

# set catchability coefficient (q)
q_list <- seq(0,1,1/(tech_num-1))

q_array <- array(q_list, c(tech_num,species_num, year))

# set effort
E_list <- seq(0,1,1/(tech_num-1))

E_array <- array(E_list, c(tech_num,species_num, year))

```

We will keep our model simple first.  Here we create a model of `r tech_num` technologies and `r species_num` species for a study period of `r year` years. The price of fish only depends on species (will add in more attributes later).


```{r}

test <- stock_size_fx(r = r_array, K = K_array, q = q_array, E = E_array)

stock_size_fx <- function(r = 0.1, K = 1, X0 = 0.1, years = 100, q = 0.01, E = 1, p = 1){
 
  ## Stock size ##
  # per species per tech
  stock_spt <- vector(length = years)
  stock_spt[1] <- X0
  # And write a stock size equation
  for(tech in 1:tech_num){
    for(sp in 1:species_num){
      for(y in 2:years){
        stock_spt[y] = stock_spt[y-1] + (r*stock_spt[y-1])*(1-(stock_spt[y-1]/K)) - q*E*stock_spt[y-1]
      
        stock_sp[sp] = sum(stock_spt[y]$sp)
        
        stock_t[tech] = sum(stock_sp[sp]$tech)
      }
    }
  }
}

#set params
 

 
  ## Harvest ##
  # Create harvest per species vector:
  harvest_sp <- vector(length = years)
  stock_sp[1] <- 0
  # And write an equation...
  for(y in 2:years){
    harvest_sp[y] = q*E*stock_sp[y]
  }
  
  # Creat harvest per technology vector:
  harvest_t <- vector(length = years)
  stock_sp[1] <- 0
  # And write an equation...
  for(y in 2:years){
    harvest_t[y] = q*E*stock_sp[y]
  }
  
  
  
  ## Profit
  # Create profit vector
  pft <- vector(length = y)
  pft[1] = 0
  # Write an equation...
  for(y in 2:years){
    pft[y] = p*harvest[y] - c*E
  }
  
  data.frame(year = seq(1, years, by = 1), 
             stock = stock, 
             harvest = harvest, 
             revenue = revenue)
}

  stock_value <- matrix(stock_value, ncol=species_num, nrow=(year+1), byrow=TRUE)
  return(stock_value)
}


```

2. Catchability Coefficient Matrix

```{r}
q_matrix <- matrix(q, nrow = tech_num, ncol = species_num)
species_tech_matrix <- data.frame(q_matrix)

# assign column and row names to the matrix
matrix_col_name <-  paste("species", 1:species_num, sep = " ")
colnames(species_tech_matrix) <- matrix_col_name
matrix_row_name <-  paste("tech", 1:tech_num, sep = " ")
rownames(species_tech_matrix) <- matrix_row_name
```

```{r}
# print the catchability table 
matrix_table = kbl(species_tech_matrix, caption = "Catchability Coefficient Matrix") %>% 
  kable_classic(full_width = F, html_font = "Cambria")
matrix_table
```



3. Calculate Stock Dynamics

```{r}
simulated_stock_dynamic <- stock_dynamic(E)
simul_stock_dynamic <- data.frame(simulated_stock_dynamic)
```

```{r}
# create the column names and row names for the simulated result
stock_col_name <-  paste("stock", 1:species_num, sep = " ")
stock_row_name <-  paste("year", 0:(year), sep = " ")

colnames(simul_stock_dynamic) <- stock_col_name
rownames(simul_stock_dynamic) <- stock_row_name

# print the first and last 5 lines of the stock dynamic dataframe in a nice formet
stock_table = kbl(simul_stock_dynamic, caption = "Stock Dynamic") %>%
  kable_classic(full_width = F, html_font = "Cambria")
stock_table
```

4. Simulate Harvest<br>
4.1 Simulate the harvest for each species
```{r}
har_spe <- data.frame(harvest_species(E))

har_col_name <-  paste("stock", 1:species_num, sep = " ")
har_row_name <-  paste("year", 0:(year), sep = " ")

colnames(har_spe) <- har_col_name
rownames(har_spe) <- har_row_name
# print the first and last 5 lines of the harvest_species dataframe in a nice formet
harvest_species_table = kbl(har_spe, caption = "Harvest for each species in each year") %>%
  kable_classic(full_width = F, html_font = "Cambria")

harvest_species_table
```

&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;
4.2 Simulate the harvest for each technology
```{r}
har_tech <- harvest_tech(E)

# assign column and row names
harvest_tech_col_name <-  paste("tech", 1:tech_num, sep = " ")
harvest_tech_row_name <-  paste("year", 0:year, sep = " ")

colnames(har_tech) <- harvest_tech_col_name
rownames(har_tech) <- harvest_tech_row_name
```


```{r}
# print the first and last 5 lines of the harvest_tech dataframe in a nice formet
harvest_tech_table = kbl(har_tech, caption = "Harvest for each technology in each year") %>%
  kable_classic(full_width = F, html_font = "Cambria")

harvest_tech_table
```

5. Calculate the profit generated by each technology
```{r}
profit <- profit_tech(E)
pro <- data.frame(profit)
# create the column names and row names for the profit dataframe
profit_col_name <-  paste("tech", 1:tech_num, sep = " ")
profit_row_name <-  paste("year", 0:year, sep = " ")

colnames(pro) <- profit_col_name
rownames(pro) <- profit_row_name

pro <- data.frame(pro)

# add a column of total profit for each year
total_profit <- rowSums(pro)
pro$total_profit <- total_profit
```

```{r}
# print the first and last 5 lines of the profit dataframe in a nice formet
profit_table = kbl(pro, caption = "Profit for each technology") %>%
  kable_classic(full_width = F, html_font = "Cambria")

profit_table
```

6. Calculate PVNB
```{r}
# sum up the present values to get the PVNB
pvnb_1 <- pvnb(E)
```


&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;**The calculated PVNB is `r pvnb_1`.**

<br>
<br>

7. Find the Best Effort
```{r}
# we set the range of effort to be [0,1] apart by 0.1
E_1 <- seq(0,15,0.5)
E_2 <- seq(0,15,0.5)
```

```{r}
# generate all the E1 and E2 combinations
E_new <- NULL
for(i in 1:length(E_1)){
  for(j in 1:length(E_2)){
    E_new <- rbind(E_new, c(E_1[i], E_2[j]))
  }
}
```


```{r}
# plug in E1 and E2 to calculate PVNB
pvnb_vec <- NULL
for(i in 1:nrow(E_new)){
   tmp_E <- E_new[i,]
   tmp_pvnb <- pvnb(tmp_E)
   pvnb_vec <- append(pvnb_vec,tmp_pvnb)
}
E_new <- data.frame(E_new)
colnames(E_new) <- c("E1", "E2")
E_new$PVNB <- pvnb_vec
```

```{r}
# print the top 5 PVNBs under 2 fishing efforts
E_top5 <- E_new %>% 
  arrange(-PVNB) %>% 
  head(5)

E_top5 = kbl(E_top5, caption = "Top 5 PVNB") %>%
  kable_classic(full_width = F, html_font = "Cambria")

E_top5
```


```{r}
# plot the distribution of pvnb under E1 and E2
pvnb_grid <- ggplot()+
  geom_raster(data = E_new,
              aes(x = E1, 
              y = E2,
              fill= PVNB))

ggplotly(pvnb_grid)
```



