---
title: "Multi_Efforts"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

# Packages
library(tidyverse)
library(Matrix)
library(kableExtra)
library(ggplot2)
library(plotly)
library(lpSolve)
library(lpSolveAPI)
```

```{r}
source("stock_dynamic.R")
source("harvest_species.R")
source("harvest_tech.R")
source("profit_tech.R")
source("pvnb.R")
```

```{r} 
# First, set seed to ensure we have the same result 
set.seed(666)


# set the number of species and technologies we want to study
species_num <- 4
tech_num <- 4


# set the number of years we want to model the stock dynamic 
year = 5

# set the discount rate
delta = 0.05
rho = 1/(1+delta)


# set values for variables in the "Our Model" section
# set parameters
species <- c(1:species_num)
parameter <- data.frame(species)
parameter$r <- c(1,0.5,0.4,0.9)
parameter$K <- c(1,1.2,2,3)
parameter$X0 <- c(0.5,0.6,1,1)
parameter$p <- c(200,200,200,200)
parameter$c <- c(1,1,1,1)
parameter$delta <- c(0.05,0.05,0.05,0.05)
parameter$rho <- 1/(1+parameter$delta)

# set catchability coefficient 
coefficient <- c(0.05,0.05,0.07,0.07,
                 0.04,0.05,0.05,0.05,
                 0,0.011,0.05,0.05,
                 0,0.01,0.02,0.05)

q_matrix <- matrix(coefficient, nrow = tech_num, ncol = species_num)

species_tech_matrix <- data.frame(q_matrix, nrow = tech_num, ncol = species_num)

# set effort for each tech 
E <- c(0.5,0.5,0.05,0.05)

# set cost for each tech
C <- c(1,1,2,2)
```

```{r}
# generate map data for each combination of E1 E2 E3 and E4
E_1 <- seq(0,8,1)
E_2 <- seq(0,8,1)
E_3 <- seq(0,8,1)
E_4 <- seq(0,8,1)


```

```{r}
E_new <- NULL


for(i in 1:length(E_1)){
  for(j in 1:length(E_2)){
    for(k in 1:length(E_3)){
      for(l in 1:length(E_4)){
        E_new <- rbind(E_new, c(E_1[i],E_2[j],E_3[k],E_4[l]))
      }
    }
  }
}

```

In E_new, each column pertains to each species, and each row pertains to possible effort combos applied to each species with effort levels ranging from 0 to 8.

The below now appends the PVNB associated w/ these effort levels to this matrix of levels. (tests a bunch of scenarios)

```{r}
pvnb_vec <- NULL
for(i in 1:nrow(E_new)){
   tmp_E <- E_new[i,]
   tmp_pvnb <- pvnb(tmp_E)
   pvnb_vec <- append(pvnb_vec,tmp_pvnb)
}
E_new <- data.frame(E_new)
colnames(E_new) <- c("E1", "E2", "E3", "E4")
E_new$PVNB <- pvnb_vec
```


```{r}
E_new <- E_new %>% 
  arrange(-PVNB)

PVNB_table = kbl(E_new[c(1:10),], caption = "Top 10 PVNB under 4 types of fishing efforts") %>%
  kable_classic(full_width = F, html_font = "Cambria")

PVNB_table_E
```

Now let's do the same thing, but for all the other parameters as a sensitivity analysis!

- catchability

```{r}
# generate map data for each combination of q1 q2 q3 and q4
q_1 <- seq(0,1,0.05)
q_2 <- seq(0,1,0.05)
q_3 <- seq(0,1,0.05)
q_4 <- seq(0,1,0.05)

```

```{r}
q_new <- NULL


for(i in 1:length(q_1)){
  for(j in 1:length(q_2)){
    for(k in 1:length(q_3)){
      for(l in 1:length(q_4)){
        q_new <- rbind(q_new, c(q_1[i],q_2[j],q_3[k],q_4[l]))
      }
    }
  }
}

```

In q_new, each column pertains to each species, and each row pertains to possible catchability combos applied to each species with catchability ranging from 0 to 1.

The below now appends the PVNB associated w/ these catchabilities to this matrix of catchabilities (tests a bunch of scenarios)

```{r}
pvnb_vec <- NULL
for(i in 1:nrow(q_new)){
   tmp_q <- q_new[i,]
   tmp_pvnb <- pvnb(tmp_q)
   pvnb_vec <- append(pvnb_vec,tmp_pvnb)
}
q_new <- data.frame(q_new)
colnames(q_new) <- c("q1", "q2", "q3", "q4")
q_new$PVNB <- pvnb_vec
```


```{r}
q_new <- q_new %>% 
  arrange(-PVNB)

PVNB_table_q = kbl(q_new[c(1:10),], caption = "Top 10 PVNB under 4 types of catchabilities") %>%
  kable_classic(full_width = F, html_font = "Cambria")

PVNB_table_q
```

- r values (growth rate)

```{r}
# generate map data for each combination of r1 r2 r3 and r4
r_1 <- seq(0.05,1,0.05)
r_2 <- seq(0.05,1,0.05)
r_3 <- seq(0.05,1,0.05)
r_4 <- seq(0.05,1,0.05)

```

```{r}
r_new <- NULL


for(i in 1:length(r_1)){
  for(j in 1:length(r_2)){
    for(k in 1:length(r_3)){
      for(l in 1:length(r_4)){
        r_new <- rbind(r_new, c(r_1[i],r_2[j],r_3[k],r_4[l]))
      }
    }
  }
}

```

In r_new, each column pertains to each species, and each row pertains to possible growth rate combos applied to each species with growth rate ranging from 0.05 to 1.

The below now appends the PVNB associated w/ these growth rates to this matrix of growth rates (tests a bunch of scenarios)

```{r}
pvnb_vec <- NULL
for(i in 1:nrow(r_new)){
   tmp_r <- r_new[i,]
   tmp_pvnb <- pvnb(tmp_r)
   pvnb_vec <- append(pvnb_vec,tmp_pvnb)
}
r_new <- data.frame(r_new)
colnames(r_new) <- c("r1", "r2", "r3", "r4")
r_new$PVNB <- pvnb_vec
```


```{r}
r_new <- r_new %>% 
  arrange(-PVNB)

PVNB_table_r = kbl(r_new[c(1:10),], caption = "Top 10 PVNB under 4 types of growth rates") %>%
  kable_classic(full_width = F, html_font = "Cambria")

PVNB_table_r
```

- K values (carrying capacity)

```{r}
# generate map data for each combination of k1 k2 k3 and k4
k_1 <- seq(0.5,5,0.5)
k_2 <- seq(0.5,5,0.5)
k_3 <- seq(0.5,5,0.5)
k_4 <- seq(0.5,5,0.5)

```

```{r}
k_new <- NULL


for(i in 1:length(k_1)){
  for(j in 1:length(k_2)){
    for(k in 1:length(k_3)){
      for(l in 1:length(k_4)){
        k_new <- rbind(k_new, c(k_1[i],k_2[j],k_3[k],k_4[l]))
      }
    }
  }
}

```

In k_new, each column pertains to each species, and each row pertains to possible carrying capacity combos applied to each species with carrying capacity ranging from 0.05 to 1.

The below now appends the PVNB associated w/ these carrying capacities to this matrix of carrying capacities (tests a bunch of scenarios)

```{r}
pvnb_vec <- NULL
for(i in 1:nrow(k_new)){
   tmp_k <- k_new[i,]
   tmp_pvnb <- pvnb(tmp_k)
   pvnb_vec <- append(pvnb_vec,tmp_pvnb)
}
k_new <- data.frame(k_new)
colnames(k_new) <- c("k1", "k2", "k3", "k4")
k_new$PVNB <- pvnb_vec
```


```{r}
k_new <- k_new %>% 
  arrange(-PVNB)

PVNB_table_k = kbl(k_new[c(1:10),], caption = "Top 10 PVNB under 4 types of carrying capacities") %>%
  kable_classic(full_width = F, html_font = "Cambria")

PVNB_table_k
```

- p (prices)

```{r}
# generate map data for each combination of p1 p2 p3 and p4
p_1 <- seq(0,200,20)
p_2 <- seq(0,200,20)
p_3 <- seq(0,200,20)
p_4 <- seq(0,200,20)

```

```{r}
p_new <- NULL


for(i in 1:length(p_1)){
  for(j in 1:length(p_2)){
    for(k in 1:length(p_3)){
      for(l in 1:length(p_4)){
        p_new <- rbind(p_new, c(p_1[i],p_2[j],p_3[k],p_4[l]))
      }
    }
  }
}

```

In p_new, each column pertains to each species, and each row pertains to possible price combos applied to each species with price ranging from 0 to 200.

The below now appends the PVNB associated w/ these prices to this matrix of prices (tests a bunch of scenarios)

```{r}
pvnb_vec <- NULL
for(i in 1:nrow(p_new)){
   tmp_p <- p_new[i,]
   tmp_pvnb <- pvnb(tmp_p)
   pvnb_vec <- append(pvnb_vec,tmp_pvnb)
}
p_new <- data.frame(p_new)
colnames(p_new) <- c("p1", "p2", "p3", "p4")
p_new$PVNB <- pvnb_vec
```


```{r}
p_new <- p_new %>% 
  arrange(-PVNB)

PVNB_table_p = kbl(p_new[c(1:10),], caption = "Top 10 PVNB under 4 different prices") %>%
  kable_classic(full_width = F, html_font = "Cambria")

PVNB_table_p
```

- c (costs)

```{r}
# generate map data for each combination of C1 C2 C3 and C4
C_1 <- seq(1,10,1)
C_2 <- seq(1,10,1)
C_3 <- seq(1,10,1)
C_4 <- seq(1,10,1)

```

```{r}
C_new <- NULL


for(i in 1:length(C_1)){
  for(j in 1:length(C_2)){
    for(k in 1:length(C_3)){
      for(l in 1:length(C_4)){
        C_new <- rbind(C_new, c(C_1[i],C_2[j],C_3[k],C_4[l]))
      }
    }
  }
}

```

In C_new, each column pertains to each technology, and each row pertains to possible cost combos applied to each tech with cost ranging from 1 to 10.

The below now appends the PVNB associated w/ these costs to this matrix of costs (tests a bunch of scenarios)

```{r}
pvnb_vec <- NULL
for(i in 1:nrow(C_new)){
   tmC_C <- C_new[i,]
   tmC_Cvnb <- pvnb(tmC_C)
   pvnb_vec <- append(pvnb_vec,tmC_Cvnb)
}
C_new <- data.frame(C_new)
colnames(C_new) <- c("C1", "C2", "C3", "C4")
C_new$PVNB <- pvnb_vec
```


```{r}
C_new <- C_new %>% 
  arrange(-PVNB)

PVNB_table_C = kbl(C_new[c(1:10),], caption = "Top 10 PVNB under 4 different costs") %>%
  kable_classic(full_width = F, html_font = "Cambria")

PVNB_table_C
```

- X0 (initial stock size)


```{r}
# generate map data for each combination of x01 x02 x03 and x04
x0_1 <- seq(1,10,1)
x0_2 <- seq(1,10,1)
x0_3 <- seq(1,10,1)
x0_4 <- seq(1,10,1)

```

```{r}
x0_new <- NULL


for(i in 1:length(x0_1)){
  for(j in 1:length(x0_2)){
    for(k in 1:length(x0_3)){
      for(l in 1:length(x0_4)){
        x0_new <- rbind(x0_new, c(x0_1[i],x0_2[j],x0_3[k],x0_4[l]))
      }
    }
  }
}

```

In x0_new, each column pertains to each species, and each row pertains to possible initial stock combos applied to each species with initial stock ranging from 1 to 10.

The below now appends the PVNB associated w/ these initial stocks to this matrix of initial stocks (tests a bunch of scenarios)

```{r}
pvnb_vec <- NULL
for(i in 1:nrow(x0_new)){
   tmx0_x0 <- x0_new[i,]
   tmx0_x0vnb <- pvnb(tmx0_x0)
   pvnb_vec <- append(pvnb_vec,tmx0_x0vnb)
}
x0_new <- data.frame(x0_new)
colnames(x0_new) <- c("x01", "x02", "x03", "x04")
x0_new$PVNB <- pvnb_vec
```


```{r}
x0_new <- x0_new %>% 
  arrange(-PVNB)

PVNB_table_x0 = kbl(x0_new[c(1:10),], caption = "Top 10 PVNB under 4 different initial stocks") %>%
  kable_classic(full_width = F, html_font = "Cambria")

PVNB_table_x0
```