---
title: ""
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

# Packages
library(tidyverse)
library(Matrix)
library(kableExtra)
```



<center><h1>Multi-Species Fishery Model</h1></center>

<center><p>This is a multi-species fishery model that allows us to reflect how quota baskets affect stock levels</p></center>

<br>

### Our Model: Population Growth & Revenue
<br>
<center><p>**Stock$_{t+1}$ = Stock$_t$ $+$ Stock$_t$ growth $-$ Harvest: **</p></center>

<center><p><mark>$X_{t+1} = X_t + rX_t\times (1-{X_t\over K}) - H_t$</mark></p></center>

<center><p>**Harvest:**</p></center>

<center><p><mark>$H_t = qX_tE_t$</mark></p></center>

<center><p>**Revenue = Price $\times$ Harvest $-$ Cost:**</p></center>

<center><p><mark>$\pi_t = p \times H_t - c$</mark></p></center>
*where,*<br>

- *$X_0$ = initial population size*<br>

- *$r$ = intrinsic growth rate*<br>

- *$K$ = carrying capacity*<br>

- *$q$ = catchability coefficient*<br>

- *$E$ = fishing effort*<br>

- *$p$ = price of 1 unit of fish*<br>

- *$\pi$ = revenue* <br>

- *$c$ = cost*<br>

<br>

### Check Our Model for Single Species

```{r, echo=FALSE}
stock_size_fx <- function(r = 0.1, K = 1, X0 = 0.1, years = 100, q = 0.01, E = 1, p = 1){
 
  ## Stock size ##
  # Create a stock size vector
  stock <- vector(length = years)
  stock[1] <- X0
  # And write a stock size equation
  for(y in 2:years){
    stock[y] = stock[y-1] + (r*stock[y-1])*(1-(stock[y-1]/K)) - q*E*stock[y-1]
  }
  
  ## Harvest ##
  # Create harvest vector:
  harvest <- vector(length = years)
  stock[1] <- 0
  # And write an equation...
  for(y in 2:years){
    harvest[y] = q*E*stock[y]
  }
  ## Profit
  # Create profit vector
  revenue <- vector(length = y)
  revenue[1] = 0
  # Write an equation...
  for(y in 2:years){
    revenue[y] = p*stock[y]
  }
  
  data.frame(year = seq(1, years, by = 1), 
             stock = stock, 
             harvest = harvest, 
             revenue = revenue)
}

test <- stock_size_fx(0.1, 1, 0.1, 100, 0.01, 1, 1)
plot(test)
```

**Great, this works for a single species. Can we include this for multiple species? **

We will need to define parameters for each of these species. We can do this by creating a list of:

* r, K, X0, years, q, E, p 

Then, we can write a function that allows us to plug these parameters in as a list of values, as many times as we want.

```{r, echo=FALSE}
# We first need to define species parameters 
params1 = list(0.1, 1, 0.1, 100, 0.01, 1, 1)
params2 = list(0.1, 5, 0.1, 100, 0.01, 1, 1)


multi_speciesfx <- function(...){
  # Define input arguments as a list to use with lapply later
  x = list(...)

  dcfx <- function(y){
    # This applies a function over a vector of parameters...
    # Unlist the params so we can plug them into our fx
    unlist(y)
    # do.call runs the function for certain parameters
    do.call(stock_size_fx, y)
  }
    # Apply it to every set of parameters
    lapply(x, dcfx)
  }

ms_test <- multi_speciesfx(params1, params2)

```

<br>

### Maxmize Revenue

```{r}
# To maxmize the revenue, we need to create a catchability coefficient matrix first. 

# First, set seed to ensure we have the same result 
set.seed(666)


# set the number of species and technologies
species_num <- 4
tech_num <- 10


# set the number of years we want to model the stock dynamic 
year = 50


# set parameters for variables in the "Our Model" section
X0 = runif(species_num, max = 1, min = 0.1)

r = runif(species_num, max = 0.8, min = 0.1)

K = runif(species_num, max = 5, min = 1)

p = runif(species_num, max = 350, min = 50)

q = runif(species_num*tech_num, max = 0.01, min = 0)

c = runif(tech_num, min = 0.2, max = 8)

E = runif(tech_num, min = 0.1, max = 6)

```

1. Imagine a *Species-Technology Catchability Coefficient Matrix*, and the cost and effort for each technology are given. Here, we create a model for `r species_num` species and `r tech_num` technologies.

```{r}
# randomly generate q (catchability coefficient) to the matrix
species_tech_matrix <- data.frame(matrix(q, nrow = tech_num, ncol = species_num))

# assign column and row names to the matrix
matrix_col_name <-  paste("species_", 1:species_num, sep = "")
colnames(species_tech_matrix) <- matrix_col_name

matrix_row_name <-  paste("tech_", 1:tech_num, sep = "")
rownames(species_tech_matrix) <- matrix_row_name

```

```{r}
# Addin cost and effort for each technology. 


# randomly generate the cost, then append the cost to our catchability dataframe
species_tech_matrix$cost <- c


# randomly generate the effort ,then append the effort to our catchability dataframe
species_tech_matrix$effort <- E
```

```{r}
# print the catchability table in a nice formet 
matrix_table = kbl(species_tech_matrix, caption = "Catchability Coefficient Matrix") %>% 
  kable_classic(full_width = F, html_font = "Cambria")
matrix_table
```

<br>

2. Simulate the stock sizes for each of the `r species_num` species and `r tech_num` technologies for a period of `r year` years. Here are the first and last 5 lines of the simulated result. 

```{r}
# write a function to calculate the stock dynamic
stock_dynamic <- function(species_index, 
                          year, 
                          r, 
                          K, 
                          X0){
  
  stock= NULL
  stock=append(stock, X0)
  
  for( i in 2:year){
    
  # apply the first equation in the "Our Model" section
  X = stock[i-1]+r*stock[i-1]*(1-stock[i-1]/K) - sum(species_tech_matrix[species_index]*species_tech_matrix$effort)*stock[i-1] 
  
  stock=append(stock, X)
  
  }
  return(stock)
}
```

```{r}
# use the function above to simulate the stock dynamics for the 4 species
simulated_stock_dynamic = NULL

for(i in 1:length(r)){
  stock = stock_dynamic(species_index = i, 
                        year = year, 
                        r = r[i], 
                        K = K[i], 
                        X0 = X0[i])
  
  simulated_stock_dynamic = cbind(simulated_stock_dynamic, stock)
  
}

```

```{r}
# turn the simulated result into a dataframe
simulated_stock_dynamic <- data.frame(simulated_stock_dynamic)

# create the column names and row names for the simulated result
stock_col_name <-  paste("stock_", 1:length(r), sep = "")

stock_row_name <-  paste("year_", 1:year, sep = "")

colnames(simulated_stock_dynamic) <- stock_col_name

rownames(simulated_stock_dynamic) <- stock_row_name
```

```{r}
# print the first and last 5 lines of the stock dynamic dataframe in a nice formet 
stock_table = kbl(simulated_stock_dynamic[c(1:5, (year-4):year),], caption = "Stock Dynamic") %>% 
  kable_classic(full_width = F, html_font = "Cambria")
stock_table
```

<br>

3. Simulate the harvest for each species 
```{r}
#calculate the harvest for the each of the species
harvest = NULL

for(i in 1:species_num){
  # apply the second equation in the "Our Model" section
  X = sum(species_tech_matrix[i]*species_tech_matrix$effort)*simulated_stock_dynamic[i]

  harvest=c(harvest, X)

}

harvest = data.frame(harvest)
```


```{r}
# print the first and last 5 lines of the harvest dataframe in a nice formet 
harvest_table = kbl(harvest[c(1:5, (year-4):year),], caption = "Harvest for each species") %>% 
  kable_classic(full_width = F, html_font = "Cambria")

harvest_table
```

<br>


4. Simulate the profit generated by each technology
```{r}
# calculate the cost for each technology 
cost_tech <- species_tech_matrix$cost * species_tech_matrix$effort
```


```{r}
# write a function to calculate the profit for each technology
profit_tech <- function(tech_index){
  
  # apply the third equation in "Our Model" section
  profit_tech_species = species_tech_matrix[tech_index, 1]*species_tech_matrix$effort[tech_index]*simulated_stock_dynamic[1]*p[1]
  
  for(j in 2:species_num){
    x = species_tech_matrix[tech_index, j]*species_tech_matrix$effort[tech_index]*simulated_stock_dynamic[j]*p[j]
    profit_tech_species <- append(profit_tech_species,x)
  }
  profit_tech_species = data.frame(profit_tech_species)
  profit_tech = rowSums(profit_tech_species) - cost_tech[tech_index]
  return(profit_tech)
}

```

```{r}
# apply the function above to calculate the profit for all the technologies
profit = NULL

for(i in 1:tech_num){
  profit = cbind(profit, profit_tech(i))
}

profit = data.frame(profit)


# create the column names and row names for the profit dataframe
profit_col_name <-  paste("tech_", 1:tech_num, sep = "")

profit_row_name <-  paste("year_", 1:year, sep = "")

colnames(profit) <- profit_col_name

rownames(profit) <- profit_row_name

# add the total profit for each year 
total_profit <- rowSums(profit)
profit$total_profit <- total_profit
```

```{r}
# print the first and last 5 lines of the profit dataframe in a nice formet 
profit_table = kbl(profit[c(1:5, (year-4):year),], caption = "Profit for each technology") %>% 
  kable_classic(full_width = F, html_font = "Cambria")

profit_table
```

<br>
<br>
<br>
*Assumptions:*<br>
*1. $X_0$, $r$, $K$, $q$, $E$, $p$, $c$ are randomly generated*<br>
*2. $X_0$ is uniformly distributed with min = 0.1, and max = 1*<br>
*3. $r$ is uniformly distributed with min = 0.1, and max = 0.8*<br>
*4. $K$ is uniformly distributed with min = 1, and max = 5*<br>
*5. $q$ is uniformly distributed with min = 0, and max = 0.01*<br>
*6. $c$ is uniformly distributed with min = 0.2, and max = 8*<br>
*7. $E$ is uniformly distributed with min = 0.1, and max = 6*<br>
