---
title: <center>Simple Model
output: html_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

# Packages
library(tidyverse)
library(Matrix)
library(kableExtra)
library(ggplot2)
library(plotly)
library(lpSolve)
library(lpSolveAPI)
```

```{r}
source("stock_dynamic.R")
source("simulated_stock_dynamic.R")
source("harvest_species.R")
source("harvest_tech.R")
source("one_tech_harvest.R")
source("profit_tech.R")
source("profit.R")
source("pvnb.R")
```


```{r} 
# First, set seed to ensure we have the same result 
set.seed(666)


# set the number of species and technologies we want to study
species_num <- 2
tech_num <- 2


# set the number of years we want to model the stock dynamic 
year = 5

# set the discount rate
delta = 0.05
rho = 1/(1+delta)


# set values for variables in the "Our Model" section
# set parameters
species <- c(1:species_num)
parameter <- data.frame(species)
parameter$r <- c(1,0.5)
parameter$K <- c(1,1.2)
parameter$X0 <- c(0.5,0.6)
parameter$p <- c(200,200)
parameter$c <- c(1,1)
parameter$delta <- c(0.05,0.05)
parameter$rho <- 1/(1+parameter$delta)

# set catchability coefficient 
coefficient <- c(0.05,0.05,
                 0.04,0.05)

# set effort for each tech 
E <- c(0.5,0.5)

# set cost for each tech
C <- c(1,1)
```

We will keep our model simple first.  Here we create a model of `r tech_num` technologies and `r species_num` species for a study period of `r year` years. The price of fish only depends on species (will add in more attributes later).

1. Initial Parameters for Species
```{r}
# print the parameter table
par <- kbl(parameter, caption = " ") %>% 
  kable_classic(full_width = F, html_font = "Cambria")
par
```

2. Catchability Coefficient Matrix

```{r}
species_tech_matrix <- data.frame(matrix(coefficient, nrow = tech_num, ncol = species_num))

# assign column and row names to the matrix
matrix_col_name <-  paste("species", 1:species_num, sep = " ")
colnames(species_tech_matrix) <- matrix_col_name
matrix_row_name <-  paste("tech", 1:tech_num, sep = " ")
rownames(species_tech_matrix) <- matrix_row_name
```

```{r}
# print the catchability table 
matrix_table = kbl(species_tech_matrix, caption = "Catchability Coefficient Matrix") %>% 
  kable_classic(full_width = F, html_font = "Cambria")
matrix_table
```



3. Calculate Stock Dynamics

```{r}
simul_stock_dynamic <- data.frame(simulated_stock_dynamic(E))
```

```{r}
# create the column names and row names for the simulated result
stock_col_name <-  paste("stock", 1:species_num, sep = " ")
stock_row_name <-  paste("year", 1:year, sep = " ")

colnames(simul_stock_dynamic) <- stock_col_name
rownames(simul_stock_dynamic) <- stock_row_name

# print the first and last 5 lines of the stock dynamic dataframe in a nice formet
stock_table = kbl(simul_stock_dynamic[c(1:5),], caption = "Stock Dynamic") %>%
  kable_classic(full_width = F, html_font = "Cambria")
stock_table
```

4. Simulate Harvest<br>
4.1 Simulate the harvest for each species
```{r}
har_spe <- data.frame(harvest_species(E))
colnames(har_spe) <- stock_col_name
rownames(har_spe) <- stock_row_name
# print the first and last 5 lines of the harvest_species dataframe in a nice formet
harvest_species_table = kbl(har_spe, caption = "Harvest for each species in each year") %>%
  kable_classic(full_width = F, html_font = "Cambria")

harvest_species_table
```

&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;
4.2 Simulate the harvest for each technology
```{r}
har_tech <- harvest_tech(E)

# assign column and row names
harvest_tech_col_name <-  paste("tech", 1:tech_num, sep = " ")
harvest_tech_row_name <-  paste("year", 1:year, sep = " ")

colnames(har_tech) <- harvest_tech_col_name
rownames(har_tech) <- harvest_tech_row_name
```


```{r}
# print the first and last 5 lines of the harvest_tech dataframe in a nice formet
harvest_tech_table = kbl(har_tech[c(1:5),], caption = "Harvest for each technology in each year") %>%
  kable_classic(full_width = F, html_font = "Cambria")

harvest_tech_table
```

5. Calculate the profit generated by each technology
```{r}
pro <- profit(E)

# create the column names and row names for the profit dataframe
profit_col_name <-  paste("tech", 1:tech_num, sep = " ")
profit_row_name <-  paste("year", 1:year, sep = " ")

colnames(pro) <- profit_col_name
rownames(pro) <- profit_row_name

pro <- data.frame(pro)

# add a column of total profit for each year
total_profit <- rowSums(pro)
pro$total_profit <- total_profit
```

```{r}
# print the first and last 5 lines of the profit dataframe in a nice formet
profit_table = kbl(pro[c(1:5),], caption = "Profit for each technology") %>%
  kable_classic(full_width = F, html_font = "Cambria")

profit_table
```

6. Calculate PVNB
```{r}
# sum up the present values to get the PVNB
pvnb_1 <- pvnb(pro)
```


&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;**The calculated PVNB is `r pvnb_1`.**

<br>
<br>

7. Find the Best Effort
```{r}
# we set the range of effort to be [0,1] apart by 0.1
E_1 <- seq(0,8,0.5)
E_2 <- seq(0,8,0.5)

# set a matrix of zeros to hold places of PVNBs under each combination of E1 and E2
pvnb_matrix <- matrix(rep(0, length(E_1)*length(E_2)), length(E_1), length(E_2))

```

```{r}
# plug in E1 and E2 to calculate PVNB
for(i in 1:length(E_1))
  {
  for(j in 1:length(E_2))
    {
    E_new <- c(E_1[i], E_2[j])
    simul_stock_dynamic <- data.frame(simulated_stock_dynamic(E_new))
    pro <- data.frame(profit(E_new))
    total_profit <- rowSums(pro)
    pro$total_profit <- total_profit
    PVNB <- pvnb(pro)
    pvnb_matrix[i,j] <- PVNB
    }
  }

```

```{r}
# convert the pvnb matrix into a one dimention vector 
matrix_1_dim <- matrix(pvnb_matrix, ncol = 1, nrow = length(E_1)*length(E_2))
```


```{r}
# put the value of E1 E2 and pvnb into one dataframe
E1 <- rep(E_1,length(E_2))
map_data <- data.frame(E1)

map_data$E2 <- rep(E_2,each=length(E_1))
map_data$pvnb <- matrix_1_dim
```

```{r}
# plot the distribution of pvnb under E1 and E2
pvnb_grid <- ggplot()+
  geom_raster(data = map_data,
              aes(x = E1, 
              y = E2,
              fill= pvnb))
pvnb_grid
```

```{r}

```

