---
title: "Maximization"
author: "Quota baskets"
date: "1/15/2021"
output:
  html_document:
    theme: cerulean
    toc: yes
    toc_float: yes
  pdf_document:
    toc: yes
---

**This Rmd summarizes the meeting 01/15/2021 with Chris and Nathan. **

### Abstract

1. We set the problem of quota basket for 3 species, 3 technologies and 2 QB constraints. 

2. We agree to evaluate the maximization of the problem and consider the lambdas as given.

3. It is the first to generalize the problem.

### Set Parameters
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message=F, warning=F)

# Packages
library(tidyverse)
library(Matrix)
library(kableExtra)
library(ggplot2)
library(plotly)
library(lpSolve)
library(lpSolveAPI)
library(ggpubr)
library(tinytex)
```

```{r} 
# First, set seed to ensure we have the same result 
set.seed(666)


# set the number of species and technologies we want to study
species_num <- 3
tech_num <- 3


# set the number of years we want to model the stock dynamic 
year = 3

# set the discount rate
delta = 0.05
rho = 1/(1+delta)


# set parameters
species <- c(1:species_num)
parameter <- data.frame(species)
parameter$r <- c(1,1,1)
parameter$K <- c(1,1,1)
parameter$X0 <- c(0.5,0.5,0.5)
parameter$p <- c(200,200,200)
parameter$delta <- c(0.05,0.05,0.05)
parameter$rho <- 1/(1+parameter$delta)

# set catchability coefficient 
coefficient <- c(0.05,0.04,0.04,
                 0.04,0.05,0.04,
                 0.04,0.04,0.05)
q_matrix <- matrix(coefficient, nrow = tech_num, ncol = species_num, byrow=T)

# set effort for each tech 
E <- c(0.5,0.5,0.5)

# set cost for each tech
C <- c(1,1,1)
```

We will keep our model simple. We created a model of `r tech_num` technologies and `r species_num` species for a study period of `r year` years. The price of fish depends on species (we will add in more attributes later).

```{r}
# print the parameter table
par <- kbl(parameter, caption = "Species Parameters") %>% 
  kable_classic(full_width = F, html_font = "Cambria")
par
```

```{r}
# q_matrix <- matrix(coefficient, nrow = tech_num, ncol = species_num)
species_tech_matrix <- data.frame(q_matrix)

# assign column and row names to the matrix
matrix_col_name <-  paste("species", 1:species_num, sep = " ")
colnames(species_tech_matrix) <- matrix_col_name
matrix_row_name <-  paste("tech", 1:tech_num, sep = " ")
rownames(species_tech_matrix) <- matrix_row_name
```

```{r}
# print the catchability table 
matrix_table = kbl(species_tech_matrix, caption = "Catchability Matrix") %>% 
  kable_classic(full_width = F, html_font = "Cambria")
matrix_table
```

We will evaluate this simple model under a linear and a exponential cost.

### Maximize Profit (2 species, 2 tecnologies, 1 constraint)

##### **Objective function**

$$
f(E) = 9E_1+9E_2-E_1^2{\beta_1} - E_2^2{\beta_2}
$$
s.t. :
$$
(0.05E_1 + 0.04E_2) \times X0_1 + (0.04E_1 + 0.05E_2) \times X0_2 = H
$$
<br>

#### **Solution (replacing integers)**

$$\begin{cases}
L(E, \lambda) = f(E) + \lambda(EqX0 - H)\\
{\partial L \over \partial E_1} = 9-2\beta_1E_1+0.045\lambda=0\\
{\partial L \over \partial E_2} = 9-2\beta_2E_2+0.045\lambda=0\\
{\partial L \over \partial \lambda} = 0.045E_1+0.045E_2-H=0\\
\end{cases}
$$
$$\begin{cases}
E_1 = {\beta_2H\over 0.0045(\beta_1+\beta_2)} \\
E_2 = {\beta_1H\over 0.0045(\beta_1+\beta_2)}\\
\end{cases}
$$

##### **In General (QB_H):**

Object function:
$$
f(E) = E_1(q_{11}p_1X0_1+q_{12}p_2X0_2) + E_2(q_{21}p_1X0_1+q_{22}p_2X0_2) - \beta_1E_1^2 - \beta_2E_2^2
$$
s.t.:
$$
E_1(q_{11}X0_1+q_{12}X0_2) + E_2(q_{21}X0_1+q_{22}X0_2) - H = 0
$$
<br>

**Lagrange Multiplier:**<br>

$$\begin{cases}
L(E, \lambda) = f(E) + \lambda(E_1(q_{11}X0_1+q_{12}X0_2) + E_2(q_{21}X0_1+q_{22}X0_2) - H)\\
{\partial L \over \partial E_1} = q_{11}p_1X0_1+q_{12}p_2X0_2-2\beta_1E_1 + \lambda (q_{11}X0_1+q_{12}X0_2)=0\\
{\partial L \over \partial E_2} = q_{21}p_1X0_1+q_{22}p_2X0_2-2\beta_2E_2 + \lambda (q_{21}X0_1+q_{22}X0_2)=0\\
{\partial L \over \partial \lambda} = E_1(q_{11}X0_1+q_{12}X0_2) + E_2(q_{21}X0_1+q_{22}X0_2) - H = 0\\
\end{cases}
$$
We replace the numbers for easier expressions:

$$\begin{cases}
{\partial L \over \partial E_1} = Z-2\beta_1E_1 + \lambda (M)=0\\
{\partial L \over \partial E_2} = W-2\beta_2E_2 + \lambda (N)=0\\
{\partial L \over \partial \lambda} = E_1(M) + E_2(N) - H = 0\\
\end{cases}
$$
The general solution is:

$$\begin{cases}
E_1 = {2\beta_2HM+(ZN-WM)N\over (2\beta_1N^2-2\beta_2M^2)} \\
E_2 = {2.\beta_1HN-(ZN-WM)M\over(2\beta_1N^2-2\beta_2M^2)}\\
\end{cases}
$$

### Maximize Profit (3 species, 3 technologies, 2 contraints)

Since we are doing optimization year by year, let's see how the first year goes. 
<br>

##### **Objective function**

$$
f(E) = E_1(p_1q_{11}X0_1+p_2q_{21}X0_2+p_3q_{31}X0_3) \\
+ p_1E_2(q_{12}X0_1+p_2q_{22}X0_2+p_3q_{32}X0_3) \\
+ E_3(p_1q_{13}X0_1+p_2q_{23}X0_2+p_3q_{33}X0_3) \\
- \beta_1E_1^2 - \beta_2E_2^2 - \beta_3E_3^2
$$

s.t.:
$$
p_1q_{11}X0_1E_1+p_2q_{21}X0_2E_1 + p_1q_{12}X0_1E_2+p_2q_{22}X0_2E_2 + \\
+ p_1q_{13}X0_1E_3+p_2q_{23}X0_2E_3 - Q_1 = 0 \\
$$

and 

$$
q_{31}p_3X0_3E_1 + q_{32}p_3X0_3E_2 + q_{33}p_3X0_3E_3 - Q_2 = 0
$$

<br>

#### **Lagrange maximization**
$$
L(E, \lambda) = f(E)  \\
+\lambda_1(q_{11}X0_1E_1+q_{21}X0_2E_1 + q_{12}X0_1E_2+q_{22}X0_2E_2 + \\
+ q_{13}X0_1E_3+q_{23}X0_2E_3 - Q_1) \\
+\lambda_2(q_{31}X0_3E_1 + q_{32}X0_3E_2 + q_{33}X0_3E_3 - Q_2) 
$$
**Lagrange Multiplier:**
<br>

$$
\begin{cases}
{\partial L \over \partial E_1} = p_1q_{11}X0_1+p_2q_{21}X0_2+p_3q_{31}X0_3- 2\beta_1E_1+\lambda_1(q_{11}X0_1+q_{21}X0_2) \\ 
+ \lambda_2(q_{31}X0_3) =0\\
{\partial L \over \partial E_2} = p_1q_{12}X0_1+p_2q_{22}X0_2+p_3q_{32}X0_3- 2\beta_2E_2+\lambda_1(q_{12}X0_1+q_{22}X0_2) + \\
+\lambda_2(q_{32}X0_3)=0\\
{\partial L \over \partial E_3} = p_1q_{13}X0_1+p_2q_{23}X0_2+p_3q_{33}X0_3- 2\beta_3E_3+\lambda_1(q_{13}X0_1+q_{23}X0_2) \\
+\lambda_2(q_{33}X0_3)=0\\
{\partial L \over \partial \lambda_1} = q_{11}X0_1E_1+q_{21}X0_2E_1 + q_{12}X0_1E_2+q_{22}X0_2E_2 + \\
+ q_{13}X0_1E_3+q_{23}X0_2E_3 - Q_1=0 \\
{\partial L \over \partial \lambda_2} = q_{31}X0_3E_1 + q_{32}X0_3E_2 + q_{33}X0_3E_3 - Q_2=0
\end{cases}
$$
<br>

$$
\begin{cases}
{\partial L \over \partial E_1} = p_1q_{11}X0_1+p_2q_{21}X0_2+p_3q_{31}X0_3- 2\beta_1E_1+\lambda_1(q_{11}X0_1+q_{21}X0_2) \\ 
+ \lambda_2(q_{31}X0_3) =0\\
{\partial L \over \partial E_2} = p_1q_{12}X0_1+p_2q_{22}X0_2+p_3q_{32}X0_3- 2\beta_2E_2+\lambda_1(q_{12}X0_1+q_{22}X0_2) + \\
+\lambda_2(q_{32}X0_3)=0\\
{\partial L \over \partial E_3} = p_1q_{13}X0_1+p_2q_{23}X0_2+p_3q_{33}X0_3- 2\beta_3E_3+\lambda_1(q_{13}X0_1+q_{23}X0_2) \\
+\lambda_2(q_{33}X0_3)=0\\
{\partial L \over \partial \lambda_1} = (q_{11}X0_1+q_{21}X0_2)E_1 + (q_{12}X0_1+q_{22}X0_2)E_2 + \\
+ (q_{13}X0_1+q_{23}X0_2)E_3 - Q_1=0 \\
{\partial L \over \partial \lambda_2} = q_{31}X0_3E_1 + q_{32}X0_3E_2 + q_{33}X0_3E_3 - Q_2=0
\end{cases}
$$

#### **Solution (replacing integers)**

$$
\begin{cases}
{\partial L \over \partial E_1} = 12-2\beta_1E_1 = - 0.045\lambda_1-0.02\lambda_2 \\
{\partial L \over \partial E_2} = 12-2\beta_2E_2 = - 0.045\lambda_1-0.02\lambda_2\\
{\partial L \over \partial E_3} = 12-2\beta_3E_3 = - 0.04\lambda_1-0.025\lambda_2\\
{\partial L \over \partial \lambda_1} = 0.045E_1+0.045E_2+0.04E_3=Q_1 \\
{\partial L \over \partial \lambda_2} = 0.02E_1+0.02E_2+0.025E_3=Q_2 \\
\end{cases}
$$
$$\begin{cases}
E_1 = {\beta_2(0.025Q_1+0.04Q_2)\over 0.000325(\beta_1+\beta_2)} \\
E_2 = {\beta_1(0.025Q_1+0.04Q_2)\over 0.000325(\beta_1+\beta_2)}\\
E_3 = {???}\\
\end{cases}
$$

#### **In General**

We try tp find values for the lambdas. It is easier but substracting equation 1 and 2. We found out that:

$$
\begin{cases}
\lambda_1  = {-(p_1X_1M+p_2X_2N)\over (X_1M+X_2N)} = -L\\
\lambda_2 = -p_3\\
M=q_{11}-q_{12}\\
N=q_{21}-q_{22}
\end{cases}
$$
These values allow that:

$$
\beta_1E_1=\beta_2E_2
$$

We can do the same exercise with derivatives (1,3) and (2,3) and we will find different values of lambda 1 that satisfy the following conditions:

$$
\beta_1E_1=\beta_3E_3 \\
\beta_2E_2=\beta_3E_3
$$
In all the cases, lambda 2 equals -price for species 3
$$
\lambda_2 = -p_3\\
$$
It is important to recognize the we need a single expression of lambda 1 that satisfies the 3 equations were lambda intervenes. Consequently if we substract derivatives 2 and 3 from equation 1, we can have the following expression:

$$
\beta_1E_1=\beta_2E_2+\beta_3E_3 \\
$$
To satisfy this relantionship our lambdas need to be:

$$
\begin{cases}
\lambda_1  = {-(p_1X_1A+p_2X_2B)\over (X_1A+X_2B)}=-L \\
\lambda_2 = -p_3\\
A=q_{11}-q_{12}-q_{13}\\
B=q_{21}-q_{22}-q_{23}
\end{cases}
$$

However, we are missing the use of the Q1 and Q2, if we use the previous in the following equation system:

$$
\begin{cases}
{\partial L \over \partial \lambda_1} = E_1(M) + E_2(N) + (O)E_3 - Q_1=0 \\
{\partial L \over \partial \lambda_2} = E_1(R) + E_2(S) + E_3(T) - Q_2=0
\end{cases}
$$

We found that:

$$
\begin{cases}
E_1={\beta_2 \over \beta_1}E_2+{\beta_3 \over \beta_1}E_3 \\
E_3={Q_1-E_2(HO) \over (HA)} \\
E_2={Q_2-R{\beta_3Q_1 \over \beta_1(HA)}-T{Q_1 \over (HA)} \over S+-R{\beta_3(HO) \over \beta_1(HA)}-T{(HO) \over (HA)}} \\
HO = {\beta_2 \over \beta_1}M+N \\
HA= {\beta_3 \over \beta_1}M+0 \\
M=q_{11}X_1-q_{21}X_2\\
N=q_{12}X_1-q_{22}X_2\\
O=q_{13}X_1-q_{23}X_2\\
R=q_{31}X_3\\
S=q_{32}X_3\\
T=q_{33}X_3\\
\end{cases}
$$

### Maximize Profit (2 species, 2 tecnologies, 2 constraint)

Object function:
$$
f(E) = E_1(q_{11}p_1X0_1+q_{12}p_2X0_2) + E_2(q_{21}p_1X0_1+q_{22}p_2X0_2) - \beta_1E_1^2 - \beta_2E_2^2
$$

s.t.:
$$
E_1(q_{11}X0_1) + E_2(q_{21}X0_1) - H_1 = 0 \\
E_1(q_{12}X0_2) + E_2(q_{22}X0_2) - H_2 = 0 \\
$$
<br>

**Lagrange Multiplier:**<br>

$$
\begin{cases}
L(E, \lambda) = f(E) + \lambda_1(E_1(q_{11}X0_1) + E_2(q_{21}X0_1)-H_1)+\\ \lambda_2(E_1(q_{12}X0_2) + E_2(q_{22}X0_2)-H_2)=0\\
{\partial L \over \partial E_1} = q_{11}p_1X0_1+q_{12}p_2X0_2-2\beta_1E_1 +\lambda_1q_{11}X0_1+ \lambda_2q_{12}X0_2=0\\
{\partial L \over \partial E_2} = q_{21}p_1X0_1+q_{22}p_2X0_2-2\beta_2E_2 +\lambda_1q_{21}X0_1+ \lambda_2q_{22}X0_2=0\\
{\partial L \over \partial \lambda_1} = E_1q_{11}X0_1 + E_2q_{21}X0_1-H_1 = 0\\
{\partial L \over \partial \lambda_2} = E_1q_{12}X0_2 + E_2q_{22}X0_2-H_2  = 0\\
\end{cases}
$$

If we substract (1)-(2) the values of lambda are:
$$
\begin{cases}
\lambda_1  = -p_1 \\
\lambda_2 = -p_2\\
\end{cases}
$$
Then the following relation ship applies:

$$
\beta_1E_1=\beta_2E_2\\
$$
$$
\begin{cases}

{\partial L \over \partial E_1} = q_{11}p_1X0_1+q_{12}p_2X0_2-2\beta_1E_1 +p_1q_{11}X0_1+ p_2q_{12}X0_2=0\\
{\partial L \over \partial E_2} = q_{21}p_1X0_1+q_{22}p_2X0_2-2\beta_2E_2 +p_1q_{21}X0_1+ p_2q_{22}X0_2=0\\
{\partial L \over \partial \lambda_1} = E_1q_{11}X0_1 + E_2q_{21}X0_1-H_1 = 0\\
{\partial L \over \partial \lambda_2} = E_1q_{12}X0_2 + E_2q_{22}X0_2-H_2  = 0\\
\end{cases}
$$

There can be multiple solutions...
