---
title: "Carrying capacity results"
author: "mauricio"
date: "2/27/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message=FALSE, warning=FALSE, echo=FALSE)

library(tidyverse)
library(here)
library(scales)
library(gridExtra)
library(grid)
library(kableExtra)
```

```{r}
# Read files results

# data
species_df <- read_csv(here("working_model","k explore","model run results files","species.csv"))
# data
tech_df <- read_csv(here("working_model","k explore","model run results files","tech_cost.csv"))

# general output files
output_sc1 <- read_csv(here("working_model","k explore","model run results files","output_b_carry1.csv")) %>% 
  mutate(run = "Scenario 1",
         year = seq(0,30))
output_sc2 <- read_csv(here("working_model","k explore","model run results files","output_b_carry2.csv"))%>% 
  mutate(run = "Scenario 2",
         year = seq(0,30))
output_sc3 <- read_csv(here("working_model","k explore","model run results files","output_b_carry3.csv"))%>% 
  mutate(run = "Scenario 3",
         year = seq(0,30))

# sum of profits

npv_sc1 <- read_csv(here("working_model","k explore","model run results files","NPV_b_carry1.csv")) %>% 
  mutate(run = "Scenario 1")
npv_sc2 <- read_csv(here("working_model","k explore","model run results files","NPV_b_carry2.csv")) %>% 
  mutate(run = "Scenario 2")
npv_sc3 <- read_csv(here("working_model","k explore","model run results files","NPV_b_carry3.csv")) %>% 
  mutate(run = "Scenario 3")

#Group them
all_outputs <- rbind(output_sc1, output_sc2, output_sc3) %>% 
  mutate(tot_profits = profit_per_t.t_1+profit_per_t.t_2+profit_per_t.t_3+profit_per_t.t_4+profit_per_t.t_5,
         tot_stock=stock.s_1+stock.s_2+stock.s_3+stock.s_4+stock.s_5)

NPVs <- rbind(npv_sc1, npv_sc2, npv_sc3) %>% 
  rename(total_profit=x)

```

# 1. Scenarios
<br />
In this section, we test how grouping stocks by their carrying capacity affect the profits, biomass and effort allocation. We are considering 3 species/fish have a medium carrying capacity (K = 100), and 2 species/fish with higher carrying capacity (K = 300) at time zero. 

<br />
We considered 3 arrangement for the quota baskets:<br />
- *Species with similar K:* we have a QB of normal K and a group of high K.<br />
- *The normal K species predominates in a basket:* we have a QB were the "normal K" species predominates (2 normal K and 1 high K), and the other basket has the remaining species (1 normal K and 1 high K).<br />
- *The high K species predominates in a basket:*we have a QB were the "high K" species predominates (1 normal K and 2 high K), and the other basket has the remaining species (2 normal K).
<br />

We are going to compare these arrangements in terms of biomass, efforts, ant total profits.  

## 1.1 Parameters

```{r}

# Make tables
species_table <- kable(species_df, col.names = c("Species", "r", "K", "Starting stock (X)", "price")) %>% 
  kable_classic(full_width = F)

tech_table <- kable(tech_df, col.names = c("Tech", "
                                               q1", "q2", "q3", 
                                               "q4", "q5",
                                               "cost")) %>% 
  kable_classic(full_width = F)

species_table

tech_table
```

# 2. Biomass

## 2.1 Biomass per species

```{r}
# Graph
ggplot(data = all_outputs)+
  geom_line(aes(y=stock.s_1, x=year), color="purple")+ 
  geom_line(aes(y=stock.s_2, x=year), color="royalblue")+ 
  geom_line(aes(y=stock.s_3, x=year), color="lightblue")+ 
  geom_line(aes(y=stock.s_4, x=year), color="red")+ 
  geom_line(aes(y=stock.s_5, x=year), color="orange")+ 
  theme_minimal()+
  labs(x= "Years",
         y= "Stock Level (tons)")+
  facet_wrap(~ run, nrow=2)

```

<br />

```{r}
# Graph
stocck_1gr <- ggplot(data = all_outputs, aes(y=stock.s_1, x=year, group=run, color=run))+
  geom_line()+
  theme_minimal()+
  labs(x= "Years",
         y= "Stock 1 (tons)")

stocck_2gr <- ggplot(data = all_outputs, aes(y=stock.s_2, x=year, group=run, color=run))+
  geom_line()+
  theme_minimal()+
  labs(x= "Years",
         y= "Stock 2 (tons)")

stocck_3gr <- ggplot(data = all_outputs, aes(y=stock.s_3, x=year, group=run, color=run))+
  geom_line()+
  theme_minimal()+
  labs(x= "Years",
         y= "Stock 3 (tons)")

stocck_4gr <- ggplot(data = all_outputs, aes(y=stock.s_4, x=year, group=run, color=run))+
  geom_line()+
  theme_minimal()+
  labs(x= "Years",
         y= "Stock 4 (tons)")

stocck_5gr <- ggplot(data = all_outputs, aes(y=stock.s_5, x=year, group=run, color=run))+
  geom_line()+
  theme_minimal()+
  labs(x= "Years",
         y= "Stock 5 (tons)")

grid.arrange(stocck_1gr, stocck_4gr, stocck_2gr, stocck_5gr, stocck_3gr, ncol=2, nrow= 3)
```
<br />
- Holding the rest of the variables constants, grouping only species with low K lead to its stock reduction.<br />
- In all the scenarios, high K species increase over time. A basket of only high K species, provide the best results. Baskets where high k species are not dominant, provide the worst results but their stocks still increase. <br />
- The results for the low k stocks improve if they are combined with high k stocks in the same basket.<br />

## 2.2 Total biomass in the ocean

```{r}
# Graph
ggplot(data = all_outputs, aes(y=tot_stock, x=year, group=run, color=run))+
  geom_line()+
  theme_minimal()+
  labs(x= "Years",
         y= "Stock (tons)")
  
```
<br />
- Combined baskets provide better total stocks in the short term, but baskets with dominant high k species provide better long term results.<br />

# 3. Effort

```{r}
# Graph
ggplot(data = all_outputs)+
  geom_line(aes(y=effort.t_1, x=year), color="purple")+ 
  geom_line(aes(y=effort.t_2, x=year), color="royalblue")+ 
  geom_line(aes(y=effort.t_3, x=year), color="lightblue")+ 
  geom_line(aes(y=effort.t_4, x=year), color="red")+ 
  geom_line(aes(y=effort.t_5, x=year), color="orange")+ 
  theme_minimal()+
  labs(x= "Years",
         y= "Effort (units)")+
  facet_wrap(~ run, nrow=2)

```
```{r}
# Graph
e_1gr <- ggplot(data = all_outputs, aes(y=effort.t_1, x=year, group=run, color=run))+
  geom_line()+
  theme_minimal()+
  labs(x= "Years",
         y= "Tech 1")

e_2gr <- ggplot(data = all_outputs, aes(y=effort.t_2, x=year, group=run, color=run))+
  geom_line()+
  theme_minimal()+
  labs(x= "Years",
         y= "Tech 2")

e_3gr <- ggplot(data = all_outputs, aes(y=effort.t_3, x=year, group=run, color=run))+
  geom_line()+
  theme_minimal()+
  labs(x= "Years",
         y= "Tech 3")

e_4gr <- ggplot(data = all_outputs, aes(y=effort.t_4, x=year, group=run, color=run))+
  geom_line()+
  theme_minimal()+
  labs(x= "Years",
         y= "Tech 4")

e_5gr <- ggplot(data = all_outputs, aes(y=effort.t_5, x=year, group=run, color=run))+
  geom_line()+
  theme_minimal()+
  labs(x= "Years",
         y= "Tech 5")

grid.arrange(e_1gr, e_4gr, e_2gr, e_5gr, e_3gr, ncol=2, nrow= 3)
```

<br />
- In Scenario 1 and Scenario 3, the efforts per technology are uniform. <br />
- When low K stocks dominate a basket, the effort that favor their catchability descends. In contrast, the efforts that favor the catch of high K species increases along with its stocks. <br />

# 4. Profit

# 4.1 Profit per technology
```{r}
# Graph
ggplot(data = all_outputs)+
  geom_line(aes(y=profit_per_t.t_1, x=year), color="purple")+ 
  geom_line(aes(y=profit_per_t.t_2, x=year), color="royalblue")+ 
  geom_line(aes(y=profit_per_t.t_3, x=year), color="lightblue")+ 
  geom_line(aes(y=profit_per_t.t_4, x=year), color="red")+ 
  geom_line(aes(y=profit_per_t.t_5, x=year), color="orange")+ 
  theme_minimal()+
  labs(x= "Years",
         y= "Profit (dollars)")+
  facet_wrap(~ run, nrow=2)

```
```{r}
# Graph
p_1gr <- ggplot(data = all_outputs, aes(y=profit_per_t.t_1, x=year, group=run, color=run))+
  geom_line()+
  theme_minimal()+
  labs(x= "Years",
         y= "Profit (tech 1)")

p_2gr <- ggplot(data = all_outputs, aes(y=profit_per_t.t_2, x=year, group=run, color=run))+
  geom_line()+
  theme_minimal()+
  labs(x= "Years",
         y= "Profit (tech 2)")

p_3gr <- ggplot(data = all_outputs, aes(y=profit_per_t.t_3, x=year, group=run, color=run))+
  geom_line()+
  theme_minimal()+
  labs(x= "Years",
         y= "Profit (tech 3)")

p_4gr <- ggplot(data = all_outputs, aes(y=profit_per_t.t_4, x=year, group=run, color=run))+
  geom_line()+
  theme_minimal()+
  labs(x= "Years",
         y= "Profit (tech 4)")

p_5gr <- ggplot(data = all_outputs, aes(y=profit_per_t.t_5, x=year, group=run, color=run))+
  geom_line()+
  theme_minimal()+
  labs(x= "Years",
         y= "Profit (tech 5)")

grid.arrange(p_1gr, p_4gr, p_2gr, p_5gr, p_3gr, ncol=2, nrow= 3)
```

<br />
- The profits from tecnologies good at catching low K species increases in baskets with only low K species.<br />
- The profits from tecnologies good at catching high K species improve in all scenarios, but present better results if they do not dominate any basket. <br />

# 4.2 Total profit per scenario

```{r}
# Graph
ggplot(data = all_outputs, aes(y=tot_profits, x=year, group=run, color=run))+
  geom_line()+
  theme_minimal()+
  labs(x= "Years",
         y= "Profit (dollars)")

```

<br />
- Scenario 1 has the best results in total profits for all the period of analysis.<br />

# 5. Summary

**Stocks**
<br />
- Holding the rest of the variables constants, grouping only species with low K lead to its stock reduction.<br />
- In all the scenarios, high K species increase over time. A basket of only high K species, provide the best results. Baskets where high k species are not dominant, provide the worst results but their stocks still increase. <br />
- The results for the low k stocks improve if they are combined with high k stocks in the same basket.<br />
- Combined baskets provide better total stocks in the short term, but baskets with dominant high k species provide better long term results.<br />

**Effort** 
<br />
- In Scenario 1 and Scenario 3, the efforts per technology are uniform. <br />
- When low K stocks dominate a basket, the effort that favor their catchability descends. In contrast, the efforts that favor the catch of high K species increases along with its stocks. <br />


**Profit** 
<br />
- The profits from tecnologies good at catching low K species increases in baskets with only low K species.<br />
- The profits from tecnologies good at catching high K species improve in all scenarios, but present better results if they do not dominate any basket. <br />
<br />
- Scenario 1 has the best results in total profits for all the period of analysis.<br />


