---
title: "analysis: 4spec fast slow tech cost"
author: "Kat Leigh"
date: "3/3/2021"
output: html_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)

library(tidyverse)
library(ggplot2)
library(here)
library(quadprog)
library(scales)
library(gridExtra)
library(grid)
library(patchwork)
```


# read in the data for best in NPV, best in av profit, and best in avstock for each assignment of species to prices.

```{r}
# get specific data for run spec 1122 def
setwd("C:/Users/kleigh/OneDrive/Documents/UCSB/quotabasket_model/working_model/price and cost explore/model run result files/4spec/costs/def/cdef1122/")
temp = list.files(pattern="*.csv")
for (i in 1:length(temp))
  {assign(paste("runz", temp[i], sep = "."), read_csv(temp[i]))}

```

```{r}
# get specific data for run ident spec 2211
setwd("C:/Users/kleigh/OneDrive/Documents/UCSB/quotabasket_model/working_model/price and cost explore/model run result files/4spec/costs/ident/cident1122/")
temp = list.files(pattern="*.csv")
for (i in 1:length(temp))
  {assign(paste("runz", temp[i], sep = "."), read_csv(temp[i]))}

```

```{r}
# get specific data for uni def

uni_def <- read_csv("C:/Users/kleigh/OneDrive/Documents/UCSB/quotabasket_model/working_model/price and cost explore/model run result files/uniident/unidef/4spec_opt_NPV_uni_def20.20.20.20.csv")

```

```{r}
# get control data (uni ident)

control <- read_csv("C:/Users/kleigh/OneDrive/Documents/UCSB/quotabasket_model/working_model/price and cost explore/model run result files/uniident/uniident/4spec_opt_NPV_uni_ident20.20.20.20.csv")

```

# choose which assignment to focus on via exploratory graphs of all inputs for each of the 3 categories

- NPV graph (all assigns)

```{r}

# NPV

names_col<- c("s_1", #"s_2"
              "s_3", "s_4", "s_5", "pft_t1", #"pft_t2",
              "pft_t3", "pft_t4", "pft_t5", "mort_1", "mort_2", "tot_pft", "tot_biomass", "run")

cntrol <- mget(ls(pattern="control")) %>% 
  as.data.frame() %>% 
  select(-contains("s_1."),
         -contains("s_3."),
         -contains("s_4."),
         -contains("s_5."),
         -contains("t_3."),
         -contains("t_4."),
         -contains("t_5."),
         -contains("t_1.1"),
         -contains("t_2.3"),
         -contains("t_2.1.1"),
         -contains("t_2.2.1")) %>% 
  mutate(run = "control")

uni_defs <- uni_def %>% 
  select(-contains("s_1."),
         -contains("s_3."),
         -contains("s_4."),
         -contains("s_5."),
         -contains("t_3."),
         -contains("t_4."),
         -contains("t_5."),
         -contains("t_1.1"),
         -contains("t_2.3"),
         -contains("t_2.1.1"),
         -contains("t_2.2.1")) %>%  
  mutate(run = "uni_def")

match_spec_slow_low <- mget(ls(pattern=".c1.1.2.2")) %>% 
  as.data.frame() %>% 
 select(-contains("s_1."),
         -contains("s_3."),
         -contains("s_4."),
         -contains("s_5."),
         -contains("t_3."),
         -contains("t_4."),
         -contains("t_5."),
         -contains("t_1.1"),
         -contains("t_2.3"),
         -contains("t_2.1.1"),
         -contains("t_2.2.1")) %>% 
  mutate(run = "match_slow_low")

match_spec_slow_high <- mget(ls(pattern="c2.2.1.1")) %>% 
  as.data.frame() %>% 
 select(-contains("s_1."),
         -contains("s_3."),
         -contains("s_4."),
         -contains("s_5."),
         -contains("t_3."),
         -contains("t_4."),
         -contains("t_5."),
         -contains("t_1.1"),
         -contains("t_2.3"),
         -contains("t_2.1.1"),
         -contains("t_2.2.1")) %>% 
  mutate(run = "match_slow_high")

mix_lhlh <- mget(ls(pattern="c1.2.1.2")) %>% 
  as.data.frame() %>% 
 select(-contains("s_1."),
         -contains("s_3."),
         -contains("s_4."),
         -contains("s_5."),
         -contains("t_3."),
         -contains("t_4."),
         -contains("t_5."),
         -contains("t_1.1"),
         -contains("t_2.3"),
         -contains("t_2.1.1"),
         -contains("t_2.2.1")) %>% 
  mutate(run = "mix_lhlh")

mix_hlhl <- mget(ls(pattern="c2.1.2.1")) %>% 
  as.data.frame() %>% 
 select(-contains("s_1."),
         -contains("s_3."),
         -contains("s_4."),
         -contains("s_5."),
         -contains("t_3."),
         -contains("t_4."),
         -contains("t_5."),
         -contains("t_1.1"),
         -contains("t_2.3"),
         -contains("t_2.1.1"),
         -contains("t_2.2.1")) %>%  
  mutate(run = "mix_hlhl")

ident_llhh <- mget(ls(pattern="ident_c1.1.2.2")) %>% 
  as.data.frame() %>% 
  select(-contains("s_1."),
         -contains("s_3."),
         -contains("s_4."),
         -contains("s_5."),
         -contains("t_3."),
         -contains("t_4."),
         -contains("t_5."),
         -contains("t_1.1"),
         -contains("t_2.3"),
         -contains("t_2.1.1"),
         -contains("t_2.2.1")) %>% 
  mutate(run = "ident_llhh")

ident_hhll <- mget(ls(pattern="ident_c2.2.1.1")) %>% 
  as.data.frame() %>% 
 select(-contains("s_1."),
         -contains("s_3."),
         -contains("s_4."),
         -contains("s_5."),
         -contains("t_3."),
         -contains("t_4."),
         -contains("t_5."),
         -contains("t_1.1"),
         -contains("t_2.3"),
         -contains("t_2.1.1"),
         -contains("t_2.2.1")) %>% 
  mutate(run = "ident_hhll")

ident_hlhl <- mget(ls(pattern="ident_c2.1.2.1")) %>% 
  as.data.frame() %>% 
 select(-contains("s_1."),
         -contains("s_3."),
         -contains("s_4."),
         -contains("s_5."),
         -contains("t_3."),
         -contains("t_4."),
         -contains("t_5."),
         -contains("t_1.1"),
         -contains("t_2.3"),
         -contains("t_2.1.1"),
         -contains("t_2.2.1")) %>%  
  mutate(run = "ident_hlhl")

ident_lhlh <- mget(ls(pattern="ident_c1.2.1.2")) %>% 
  as.data.frame() %>% 
  select(-contains("s_1."),
         -contains("s_3."),
         -contains("s_4."),
         -contains("s_5."),
         -contains("t_3."),
         -contains("t_4."),
         -contains("t_5."),
         -contains("t_1.1"),
         -contains("t_2.3"),
         -contains("t_2.1.1"),
         -contains("t_2.2.1")) %>% 
  mutate(run = "ident_lhlh")


names(cntrol) <- names_col
names(uni_defs) <- names_col
# names(match_spec_slow_high) <- names_col
# names(match_spec_slow_low) <- names_col
# names(mix_lhlh) <- names_col
# names(mix_hlhl) <- names_col
names(ident_llhh) <- names_col
names(ident_hhll) <- names_col
names(ident_lhlh) <- names_col
names(ident_hlhl) <- names_col

```

```{r}

mixapart1 <- mix_hlhl %>% 
  select(1:12) %>% 
  mutate(run = 'mix_hlhl')
names(mixapart1) <- names_col

mixapart2 <- mix_hlhl %>% 
  select(13:24) %>% 
  mutate(run = 'mix_hlhl')
names(mixapart2) <- names_col

mix_hlhl <- do.call(rbind, mget(ls(pattern= 'mixapart.'))) %>% 
  mutate(verz = c(rep(1,31),rep(2,31))) %>% 
  filter(verz == 1)

mixapart1 <- mix_lhlh %>% 
  select(1:12) %>% 
  mutate(run = 'mix_lhlh')
names(mixapart1) <- names_col

mixapart2 <- mix_lhlh %>% 
  select(13:24) %>% 
  mutate(run = 'mix_lhlh')
names(mixapart2) <- names_col

mix_lhlh <- do.call(rbind, mget(ls(pattern= 'mixapart.')))%>% 
  mutate(verz = c(rep(1,31),rep(2,31))) %>% 
  filter(verz == 1)

mixapart1 <- match_spec_slow_high %>% 
  select(1:12) %>% 
  mutate(run = 'match_hhll')
names(mixapart1) <- names_col

mixapart2 <- match_spec_slow_high %>% 
  select(13:24) %>% 
  mutate(run = 'match_hhll')
names(mixapart2) <- names_col

match_spec_slow_high <- do.call(rbind, mget(ls(pattern= 'mixapart.')))%>% 
  mutate(verz = c(rep(1,31),rep(2,31))) %>% 
  filter(verz == 1)

mixapart1 <- match_spec_slow_low %>% 
  select(1:12) %>% 
  mutate(run = 'match_llhh')
names(mixapart1) <- names_col

mixapart2 <- match_spec_slow_low %>% 
  select(13:24) %>% 
  mutate(run = 'match_llhh')
names(mixapart2) <- names_col

match_spec_slow_low <- do.call(rbind, mget(ls(pattern= 'mixapart.')))%>% 
  mutate(verz = c(rep(1,31),rep(2,31))) %>% 
  filter(verz == 1)

uni_defs <- uni_defs %>% 
  mutate(verz = '0u')

cntrol <- cntrol %>% 
  mutate(verz = '0c')

ident_hhll <- ident_hhll %>% 
  mutate(verz = 'ident_runz')

ident_hlhl <- ident_hlhl %>% 
  mutate(verz = 'ident_runz')

ident_lhlh <- ident_lhlh %>% 
  mutate(verz = 'ident_runz')

ident_llhh <- ident_llhh %>% 
  mutate(verz = 'ident_runz')

v1 <- ls(pattern = "uni_defs|cntrol|mix_|match_|ident_l|ident_h")

v2 <- do.call(rbind,mget(v1))

v2 <- v2 %>% 
  mutate(linetype = case_when(grepl("control", run) ~ "identuni",
                              grepl("uni", run) ~ "diffuni",
                              grepl("match.", run) ~ "match",
                              grepl("mix", run) ~ "mix",
                              grepl("ident", run)~ "ident"))

v2 <- v2 %>% 
  mutate(run = case_when(grepl("control", run) ~ "identical species, uniform costs: $1",
                              grepl("uni", run) ~ "2 slow-growing species, 2 fast-growing, uniform costs",
                              grepl("match_hh", run) ~ "2 slow-growing with high costs",
                              grepl("match_ll", run) ~ "2 slow-growing with low costs",
                              grepl("mix_hl", run) ~ "sp1: high, sp3: low, sp4: high, sp5: low",
                              grepl("mix_lh", run) ~ "sp1: low, sp3: high, sp4: low, sp5: high",
                              grepl("ident_hh", run) ~ "identical species with high costs",
                              grepl("ident_ll", run) ~ "identical species with low costs",
                              grepl("ident_hl", run) ~ "identical species, sp1: high, sp3: low, sp4: high, sp5: low",
                              grepl("ident_lh", run) ~ "identical species, sp1: low, sp3: high, sp4: low, sp5: high"
                         ))

```

# make graphs

```{r}

#run_factors <- factor(v2$run, levels = unique(v2$run),
 #                            labels = c("Ex: $20 all", "Ex: Sp1- $40", "Ex: Sp2- $40", "Ex: Sp3- $40", "Ex: Sp4- $40", "Ex: Sp5- $40"))

# tidy_av_biomass$run <- run_factors
# tidy_NPVs$run <- run_factors
# tidy_av_pft$run <- run_factors

#NPV
pft_g_NPV_v2 <- ggplot()+
  geom_smooth(data = v2, aes(y=tot_pft, x=rep(0:30,10), color = as.factor(run),
                             linetype = as.factor(linetype)), se = FALSE, na.rm = TRUE)+ theme_minimal()+
  labs(title= str_wrap("Profits for optimal-NPV arrangements, ", 80),
         x= "Number of Years",
         y= "Fishery-wide Annual Profits",
       color= "Trial Run")+
  scale_y_continuous(labels=dollar_format(prefix="$"))+
  facet_wrap(~run, labeller = labeller(run = label_wrap_gen(30)))+
  theme(plot.caption = element_text(hjust = 0))

```

what happens to each stock under these arrangements?

```{r}

longer_comp <- v2 %>%
  rownames_to_column() %>% 
  pivot_longer(cols = c(s_1:s_5, tot_biomass), names_to = "Species", values_to = "Stock_Level")

longer_comp$Species <- factor(longer_comp$Species, levels = c("s_1", #'s_2',
's_3', 's_4', 's_5', 'tot_biomass'), 
                  labels = c("Species 1", #"Species 2",
                             "Species 3", 'Species 4', 'Species 5', 'Fishery Wide'))

df <- split(longer_comp,f = longer_comp$run)

# df$`$20 all`$Species <- factor(df$`$20 all`$Species, levels = unique(df$`$20 all`$Species),
#                                   labels = c('Sp1: $20', 'Sp2: $20', 'Sp3: $20', 'Sp4: $20', 'Sp5: $20', 'Fishery Wide'))
# 
# legend_runs <- factor(df$NPV$Species, levels = unique(df$NPV$Species),
#                                   labels = c('Sp1: $1', 'Sp2: $1', 'Sp3: $1', 'Sp4: $1', 'Sp5: $40', 'Fishery Wide'))
# 
# df$`average annual biomass`$Species <- legend_runs

p1 <- ggplot(filter(df$`identical species, uniform costs: $1`, Species != "Fishery Wide"), aes(x = rep(0:30,4),y = Stock_Level, colour = Species, linetype = linetype)) + 
  geom_smooth(method = "loess", se = FALSE, formula = 'y ~ x') +  theme_minimal()+
  facet_wrap(~run, labeller = labeller(run = label_wrap_gen(30)))+
  labs(x= NULL,
       y=NULL,
       color= "Species",
       linetype=NULL)+
  scale_color_viridis_d()+
  scale_y_continuous(limits = c(0,60))+
  scale_linetype(guide = "none")

p2 <- p1 %+% filter(df$`2 slow-growing species, 2 fast-growing, uniform costs`, Species != "Fishery Wide") + theme(legend.position = "none")
p3 <- p1 %+% filter(df$`2 slow-growing with high costs`, Species != "Fishery Wide")+ theme(legend.position = "none")
p4 <- p1 %+% filter(df$`2 slow-growing with low costs`, Species != "Fishery Wide")+ theme(legend.position = "none")
p5<- p1 %+% filter(df$`sp1: high, sp3: low, sp4: high, sp5: low`, Species != "Fishery Wide")+ theme(legend.position = "none")
p6<- p1 %+% filter(df$`sp1: low, sp3: high, sp4: low, sp5: high`, Species != "Fishery Wide")+ theme(legend.position = "none")
p7<- p1 %+% filter(df$`identical species with high costs`, Species != "Fishery Wide")+ theme(legend.position = "none")
p8<- p1 %+% filter(df$`identical species with low costs`, Species != "Fishery Wide")+ theme(legend.position = "none")
p9 <- p1 %+% filter(df$`identical species, sp1: high, sp3: low, sp4: high, sp5: low`, Species != "Fishery Wide")+ theme(legend.position = "none")
p10 <-p1 %+% filter(df$`identical species, sp1: low, sp3: high, sp4: low, sp5: high`, Species != "Fishery Wide")+ theme(legend.position = "none")

stock_comp_g <- (plot_spacer()|p1|p2|plot_spacer()) / (p7|p8|p9|p10) / (p3|p4|p5|p6) + plot_annotation(
  title = str_wrap("Predicted annual stock levels for a fishery with varried technology costs under 2 quota baskets", 100),
  caption = str_wrap("Results of a 2 quota basket model for 5 species and 5 technologies parameterized such that the control has identical species and technology costs. The trials have identical species besides growth rates, and the technologies differ in their respective costs. Growth rates are: 3 species of 0.2, and 2 species of 0.3. Technology costs are either 3 at $1 and 2 at $2, or 3 at $1 and 2 at $2.", 140)
)

```

mortality analysis

```{r}

morts <- v2 %>% 
  group_by(run) %>% 
  dplyr::select(mort_1,mort_2, tot_pft:run,linetype) %>% 
  dplyr::summarise(tot_pft = mean(tot_pft, na.rm = TRUE),
            tot_biomass = mean(tot_biomass),
            mort_1 = unique(mort_1),
            mort_2 = unique(mort_2))

```



# export results

- graphs of the most interesting comparison
- summary table of results for each item in graph

