---
title: "overfished with overfished, stable with stable"
author: "Mauricio Collado"
date: "2/27/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(ggplot2)
library(here)
library(quadprog)
library(future)
```

### Preparing the inputs and outputs for `qb_stock.r`:

For each species, we need:

* r - growth rate
* K - carrying capacity
* X - starting stock
* p - price

For each technology we need:

* Catchability per species
* Cost per unit effort

# Inputs

## Step 1: Input parameters
```{r}

# the following model will test what happens:
# - when we group overexploited stocks
# - when we group stable stocks
# the rest of variables
# Species:
# s = species, r, K, X, p

s1 <- c(s=1, r=0.2, K=100, X=25, p=20) #overexploited
s2 <- c(s=2, r=0.2, K=100, X=25, p=20) #overexploited
s3 <- c(s=3, r=0.2, K=100, X=25, p=20) #overexploited
s4 <- c(s=4, r=0.2, K=100, X=50, p=20) #stable
s5 <- c(s=5, r=0.2, K=100, X=50, p=20) #stable

# t = tech, q1 = catchability species 1, q2 = catchability species 2...

t1 <- c(t=1, q1=0.04, q2=0.01, q3=0.01, q4=0.01, q5 = 0.01)
t2 <- c(t=2, q1=0.01, q2=0.04, q3=0.01, q4=0.01, q5 = 0.01)
t3 <- c(t=3, q1=0.01, q2=0.01, q3=0.04, q4=0.01, q5 = 0.01)
t4 <- c(t=4, q1=0.01, q2=0.01, q3=0.01, q4=0.04, q5 = 0.01)
t5 <- c(t=5, q1=0.01, q2=0.01, q3=0.01, q4=0.01, q5 = 0.04)

# Tech cost: t = tech, cost = cost per unit effort
c1 <- c(t=1, cost=1)
c2 <- c(t=2, cost=1)
c3 <- c(t=3, cost=1)
c4 <- c(t=4, cost=1)
c5 <- c(t=5, cost=1)

# Baskets: binary matrix of # species x # baskets, where 1 means that species is in that basket

b1 <- c(s1 = 1, s2 = 1, s3 = 1, s4 = 0, s5 = 0)
b2 <- c(s1 = 0, s2 = 0, s3 = 0, s4 = 1, s5 = 1)
# b3 <- c(s1 = 0, s2 = 0, s3 = 1, s4 = 0, s5 = 0)
# b4 <- c(s1 = 0, s2 = 0, s3 = 0, s4 = 1, s5 = 0)
# b5 <- c(s1 = 0, s2 = 0, s3 = 0, s4 = 0, s5 = 1)


# Quotas: position = basket, number is the harvest limit.
# We want this to be 0.1 of the preceding stock under constant mortality, so this will have to change to just input constant m.


# This is a guess of optimal mortality for each bakset. A good starting point is r/2.
mort_guess = c(0.2, 0.2)

# Years
years = 30
```

# Step 2: make a list of the inputs
```{r}
# Change these to reflect the number of species and technologies above:
species = list(s1, s2, s3, s4, s5)
tech = list(t1, t2, t3, t4, t5)
cost = list(c1, c2, c3, c4, c5)
baskets = list(b1, b2) #, b3, b4, b5)
```

# Step 3: Run the function

```{r}
source(here("working_model", "functions", "optimal_baskets.R"))

output <- optimal_baskets(species, tech, cost, baskets, mort_guess, years)
```

# Step 4: save results of each run


```{r}
NPV <- sum(drop_na(output$profit_per_t))
#here("health status explore") 
# I dont know why it refuses to save in my G drive
  csvname <- "output_b_x1.csv"
  #csvfile <- paste(path_store, csvname, sep="")
  csvfile <- paste(csvname, sep="")
  write.table(na.omit(output),csvfile, row.names=FALSE, sep=",")
  
#path_store <- here("health status explore") 
  csvname <- "NPV_b_x1.csv"
  #csvfile <- paste(path_store, csvname, sep="")
  csvfile <- paste(csvname, sep="")
  write.table(na.omit(NPV),csvfile, row.names=FALSE, sep=",")

```

```{r}
# tables
sp_df <- as.data.frame(do.call(rbind, species))
tech_df <- as.data.frame(do.call(rbind, tech))
cost_df <- as.data.frame(do.call(rbind, cost))
baskets_df <- as.data.frame(do.call(rbind, baskets))

tech_tbl_df <- tech_df %>% 
  inner_join(cost_df, by = "t")

csvname <- "species.csv"
csvfile <- paste(csvname, sep="")
write.table(sp_df, csvfile, row.names=FALSE, sep=",")

csvname <- "tech_cost.csv"
csvfile <- paste(csvname, sep="")
write.table(tech_tbl_df, csvfile, row.names=FALSE, sep=",")
 
```

## Step 1: Input parameters
```{r}

# Baskets: binary matrix of # species x # baskets, where 1 means that species is in that basket

b1 <- c(s1 = 1, s2 = 1, s3 = 0, s4 = 1, s5 = 0)
b2 <- c(s1 = 0, s2 = 0, s3 = 1, s4 = 0, s5 = 1)

```

# Step 2: make a list of the inputs
```{r}
# Change these to reflect the number of species and technologies above:

baskets = list(b1, b2) #, b3, b4, b5)
```

# Step 3: Run the function

```{r}
output <- optimal_baskets(species, tech, cost, baskets, mort_guess, years)
```

# Step 4: save results of each run


```{r}
NPV <- sum(drop_na(output$profit_per_t))
#here("health status explore") 
# I dont know why it refuses to save in my G drive
  csvname <- "output_b_x2.csv"
  #csvfile <- paste(path_store, csvname, sep="")
  csvfile <- paste(csvname, sep="")
  write.table(na.omit(output),csvfile, row.names=FALSE, sep=",")
  
#path_store <- here("health status explore") 
  csvname <- "NPV_b_x2.csv"
  #csvfile <- paste(path_store, csvname, sep="")
  csvfile <- paste(csvname, sep="")
  write.table(na.omit(NPV),csvfile, row.names=FALSE, sep=",")

```

## Step 1: Input parameters
```{r}
b1 <- c(s1 = 1, s2 = 0, s3 = 0, s4 = 1, s5 = 1)
b2 <- c(s1 = 0, s2 = 1, s3 = 1, s4 = 0, s5 = 0)

```

# Step 2: make a list of the inputs
```{r}

baskets = list(b1, b2) #, b3, b4, b5)
```

# Step 3: Run the function

```{r}
output <- optimal_baskets(species, tech, cost, baskets, mort_guess, years)
```

# Step 4: save results of each run


```{r}
NPV <- sum(drop_na(output$profit_per_t))
#here("health status explore") 
# I dont know why it refuses to save in my G drive
  csvname <- "output_b_x3.csv"
  #csvfile <- paste(path_store, csvname, sep="")
  csvfile <- paste(csvname, sep="")
  write.table(na.omit(output),csvfile, row.names=FALSE, sep=",")
  
#path_store <- here("health status explore") 
  csvname <- "NPV_b_x3.csv"
  #csvfile <- paste(path_store, csvname, sep="")
  csvfile <- paste(csvname, sep="")
  write.table(na.omit(NPV),csvfile, row.names=FALSE, sep=",")

```


