---
title: "5s_3t_2b"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(ggplot2)
library(here)
library(quadprog)
library(future)
```
### This is okay but it kinda sucks...



### Preparing the inputs and outputs for `qb_stock.r`:

For each species, we need:

* r - growth rate
* K - carrying capacity
* X - starting stock
* p - price

For each technology we need:

* Catchability per species
* Cost per unit effort

# Inputs

## Step 1: Input parameters
```{r}
# Species:
# s = species, r, K, X, p

s1 <- c(s=1, r=0.15, K=100, X=50, p=10) 
s2 <- c(s=2, r=0.2, K=100, X=50, p=20)
s3 <- c(s=3, r=0.2, K=100, X=50, p=8)
s4 <- c(s=4, r=0.3, K=100, X=50, p=10)
s5 <- c(s=5, r=0.4, K=100, X=50, p=12)

# t = tech, q1 = catchability species 1, q2 = catchability species 2...

t1 <- c(t=1, q1=0.04, q2=0.01, q3=0.01, q4=0.01, q5 = 0.1)
t2 <- c(t=2, q1=0.01, q2=0.04, q3=0.01, q4=0.01, q5 = 0.01)
t3 <- c(t=2, q1=0.01, q2=0.01, q3=0.04, q4=0.01, q5 = 0.01)
t4 <- c(t=2, q1=0.01, q2=0.01, q3=0.01, q4=0.04, q5 = 0.01)
t5 <- c(t=2, q1=0.01, q2=0.01, q3=0.01, q4=0.01, q5 = 0.04)

# Tech cost: t = tech, cost = cost per unit effort
c1 <- c(t=1, cost=1)
c2 <- c(t=2, cost=1)
c3 <- c(t=3, cost=1)
c4 <- c(t=4, cost=1)
c5 <- c(t=5, cost=1)

# Baskets: bimary matrix of # species x # baskets, where 1 means that species is in that basket

b1 <- c(s1 = 1, s2 = 1, s3 = 0, s4 = 0, s5 = 0)
b2 <- c(s1 = 0, s2 = 0, s3 = 1, s4 = 1, s5 = 1)


# Quotas: position = basket, number is the harvest limit.
# We want this to be 0.1 of the preceding stock under constant mortality, so this will have to change to just input constant m.

mortality = c(0.11, 0.11)

# Years
years = 30
```

# Step 2: make a list of the inputs
```{r}
# Change these to reflect the number of species and technologies above:
species = list(s1, s2, s3, s4, s5)
tech = list(t1, t2, c3, c4, c5)
cost = list(c1, c2, c3, c4, c5)
baskets = list(b1, b2)
```

# Step 3: Run the function

```{r}
qb_max_p <- function(baskets, species, tech, cost, years){
  mort <- seq(0.01, 0.5, by = 0.05)
  mort_full = expand.grid(replicate(length(baskets),mort, F))
  p_out <- data_frame(m1 = 0, m2 = 0, prof = 0)
  for(i in 1:nrow(mort_full)){
    tmp_m <- t(mort_full[i,])
    out <- qb_stock(species, tech, cost, baskets, tmp_m, years)
    total_prof <- sum(colSums(out$profit_per_t, na.rm = TRUE))
    vec <- tibble(mort_full[i,], total_prof)
    colnames(vec) <- colnames(p_out)
    p_out <- rbind(vec, p_out)
  }
  
  row_number <- which.max(p_out$prof)
  max_mort <- p_out[row_number,]
  return(max_mort[,1:2])
}

source(here("working_model", "qb_stock_m.R"))


max_p <- qb_max_p(baskets, species, tech, cost, years)



output <- qb_stock(species, tech, cost, baskets, mortality, years)

total_p <- colSums(output$profit_per_t, na.rm = TRUE)

profit_5 <- sum(total_p)
# max_p[,1:2]
# 
# output <- qb_stock(species, tech, cost, baskets, mortality, years)
# 
# output$stock ### WOOT
```
What I want this to do:

Input normal inputs EXCEPT baskets
Calculate every possible basket matrix for a matrix of those dims
Calculate the maximum mortality for each and every basket matrix
Run QB solve with the optimal mortality
Return the stock values, species, and the run number as a df.



```{r}

# Matrix combination code I shamelessly stole from online:

matrixCombn <- function(nrow, ncol) {
    # All possible column combinations for a matrix of dimension dim
    # Here we assume two different values c(1, 0)
    require(gtools);
    columns <- t(permutations(n = 2, r = nrow, v = c(1, 0), repeats.allowed = TRUE));
    columns <- columns[, colSums(columns) == 1];

    # Construct all possible combinations of dim column vectors and
    # impose constraint that row and column sum >= 1
    ret <- lapply(as.data.frame(t(permutations(ncol(columns), ncol, repeats.allowed = TRUE))), function(x) {
        m.cand <- columns[, x];
        if (all(rowSums(m.cand) > 0) & all(colSums(m.cand) > 0)) m.cand else NULL;
    })
    ret <- Filter(Negate(is.null), ret);
    return(ret);
}
```

```{r}
# Baskets and mortality needa be calculated

qb_allbaskets <- function(nBaskets, species, tech, cost, years){

  # Number of species
  n_sp <- length(species)
  
  # Empty df:
  stock_df <- data.frame(stock = 0, run = 0)
  
  # Run matrix comb for the baskets (rows) x species (columns)
  bmtx <- matrixCombn(nBaskets, n_sp)
  
  b_list <- list()
  ### YUCK  ### THIS NEEDS TO BE UPDATED EACH AND EVERY TIME
  for(i in 1:length(bmtx)){
    mx <- matrix(unlist(bmtx[i]), ncol = n_sp, nrow = nBaskets)
    
    b1 <- mx[1,]
    b2 <- mx[2,]
    # b3 <- mx[3,]
    # b4 <- mx[4,]
    # b5 <- mx[5,]
    baskets <- list(b1, b2)# # b3) #, b4, b5)
    b_list <- append(b_list, list(baskets))
  }
  
  # Start up future:
  plan(multiprocess, workers = 5)
  
  # AHHHHHH
  mort_list <- future.apply::future_lapply(b_list[20:30], qb_max_p, species = species, tech = tech, cost = cost,years = years)
  # Parallel process these
  # This is just one mortality for the whole quota
  
  run <- 0
  # Run QB stock for every matrix with max mortality
  for(i in 1:length(mort_list)){
    mx <- NULL
    vec <- NULL
    b_lst <- unlist(b_list[1], recursive = FALSE)
    b_1 <- unlist(b_lst[1])
    b_2 <- unlist(b_lst[2])
    # b_3 <- unlist(b_lst[3])
    # b_4 <- unlist(b_lst[4])
    # b_5 <- unlist(b_lst[5])
    new_bs <- list(b_1, 
                   b_2) 
                   # b_3) #, 
                   # b_4,
                   # b_5
                   #)
    mort <- unlist(mort_list[1])
    
    out <- qb_stock(species = species, tech = tech, cost = cost, baskets = new_bs, mortality = mort[1:2], years = years)
    
    # Get the ending biomasses
    last_bio <- tail(out$stock, 1)
    # Get run number
    run <- run+1
    
    vec <- rep(run, n_sp)
    mx <- as.data.frame(matrix(last_bio))
    mx <- cbind(mx, vec)
      
    colnames(mx) <- c("stock", "run")
    
    stock_df <- rbind(stock_df,mx)
  }
  
  stock_df$stock <- unlist(stock_df[,1])
  return(stock_df)
}

stock_df
plot(stock_df)

tentotwenty <- stock_df




qb_2 <- tentotwenty %>% 
  mutate(stock = as.numeric(stock)) %>% 
  mutate(baskets = 2)


write_csv(qb_2, here("working_model", "scratch", "end_biomass_5sp", "2_basket.csv"))






```





