---
title: "5s_3t_2b"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(ggplot2)
library(here)
library(quadprog)
library(future)
```
### This is okay but it kinda sucks...



### Preparing the inputs and outputs for `qb_stock.r`:

For each species, we need:

* r - growth rate
* K - carrying capacity
* X - starting stock
* p - price

For each technology we need:

* Catchability per species
* Cost per unit effort

# Inputs

## Step 1: Input parameters
```{r}
# Species:
# s = species, r, K, X, p

s1 <- c(s=1, r=0.15, K=100, X=50, p=8) 
s2 <- c(s=2, r=0.2, K=100, X=50, p=12)
s3 <- c(s=3, r=0.2, K=100, X=50, p=8)
s4 <- c(s=4, r=0.3, K=100, X=50, p=10)
s5 <- c(s=5, r=0.4, K=100, X=50, p=12)


# t = tech, q1 = catchability species 1, q2 = catchability species 2...

t1 <- c(t=1, q1=0.04, q2=0.01, q3=0.01, q4=0.01, q5 = 0.1)
t2 <- c(t=2, q1=0.01, q2=0.04, q3=0.01, q4=0.01, q5 = 0.01)
t3 <- c(t=2, q1=0.01, q2=0.01, q3=0.04, q4=0.01, q5 = 0.01)
t4 <- c(t=2, q1=0.01, q2=0.01, q3=0.01, q4=0.04, q5 = 0.01)
t5 <- c(t=2, q1=0.01, q2=0.01, q3=0.01, q4=0.01, q5 = 0.04)


# Tech cost: t = tech, cost = cost per unit effort
c1 <- c(t=1, cost=1)
c2 <- c(t=2, cost=1)
c3 <- c(t=3, cost=1)
c4 <- c(t=4, cost=1)
c5 <- c(t=5, cost=1)

# Baskets: bimary matrix of # species x # baskets, where 1 means that species is in that basket

b1 <- c(s1 = 1, s2 = 0, s3 = 0, s4 = 0, s5 = 0)
b2 <- c(s2 = 0, s2 = 1, s3 = 0, s4 = 0, s5 = 0)
b3 <- c(s3 = 0, s2 = 0, s3 = 1, s4 = 0, s5 = 0)
b4 <- c(s4 = 0, s2 = 0, s3 = 0, s4 = 1, s5 = 0)
b5 <- c(s5 = 0, s2 = 0, s3 = 0, s4 = 0, s5 = 1)


# Quotas: position = basket, number is the harvest limit.
# We want this to be 0.1 of the preceding stock under constant mortality, so this will have to change to just input constant m.

mortality = c(0.06, 0.76)

# Years
years = 30
```

# Step 2: make a list of the inputs
```{r}
# Change these to reflect the number of species and technologies above:
species = list(s1, s2, s3, s4, s5)
tech = list(t1, t2, t3, t4, t5)
cost = list(c1, c2, c3, c4, c5)
baskets = list(b1, b2, b3, b4, b5)

```

# Step 3: Run the function


This function should converge at r/2


```{r GS function}

# This finds the optimal steady state harvest point for each individual species, YAAR?

FishOpt_GS<-function(bvec,K,g,p,cost,beta,disc,tol=.1, t_end = 300){
  delta=1/(1+disc)
  #Optim objective function
  Objective<-function(f,b,bvec,K,gar,p,cost,beta,delta,V){
    r<-gar
    bnext = max(min(bvec), b + r*b*(1-b/K) - f)
    bnext = min(max(bvec), bnext) #Make sure we don't go below the minimum biomass
    profit=p*f-cost*f^beta
    Vnext = spline(x=bvec,y=V,xout=bnext)
    negout = -(profit + delta*Vnext$y)
    return(negout) # Negative profits
  }
  #Set up storage vectors and initial loop parameters
  tolcheck=10*tol
  t=0
  Vstar=rep(0,length.out=length(bvec))
  f=rep(1,length.out=length(bvec))
  #While iterate until convergence
  while(t<4|tolcheck>tol){
  t=t+1
  V=Vstar
  pastf=f
  #Loop over states
  for(i in 1:length(bvec)){
  b=bvec[i]
  if(i==1){
  guess=0
  }else{
  guess=f[i-1]
  }
  low=0.00001 ## If you get error in optim finite fn convergence issues, changes this to something positive but REALLY small 0.00001
  high=(b + g*b*(1-b/K)) #Max possible harvest is the available fish plus the growth
  Opt=optim(par=guess,fn=Objective,lower=low,upper=high,method = "L-BFGS-B",b=b,bvec=bvec,gar=g,cost=cost,K=K,p=p,V=V,beta=beta,delta=delta)
  f[i]=Opt$par
  Vstar[i]=-Opt$value
  }
  #Check tolerance in each time period, this is policy function convergence, no check for value function convergence
  tolcheck=sum(abs(f-pastf))
  if(t>t_end){
    print("Exceed Maximum time steps with tolerance remaining:")
    print(tolcheck)
    break
  }
  converge=c(t,tolcheck)
  }
  return(list(Policy=f,Value=Vstar,converge=converge))
}
```


# Step 3: make nice inputs

```{r}
sp_df <- as.data.frame(do.call(rbind, species))
tech_df <- as.data.frame(do.call(rbind, tech))
cost_df <- as.data.frame(do.call(rbind, cost))
baskets_df <- as.data.frame(do.call(rbind, baskets))
```


```{r}
bveclist=list(seq(0.1,sp_df$K[1],length.out=50), seq(0.1,sp_df$K[2],length.out=50), seq(0.1, sp_df$K[3], length.out = 50), seq(0.1,sp_df$K[4],length.out=50), seq(0.1,sp_df$K[5],length.out=50))

Klist=as.list(sp_df$K)
rlist=as.list(sp_df$r)
plist=as.list(sp_df$p)
costlist=list(1, 1, 1, 1, 1)  
betalist=list(2, 2, 2, 2, 2)
disclist=list(0,0,0,0,0)

optimal_output=pmap(list(bveclist,Klist,rlist,plist,costlist,betalist,disclist),FishOpt_GS)

optimal_output

## Pull the steady state harvest from this run:

s1h <- 4/50
s2h <- 6/50
s3h <- 4/50
s4h <- 5/50
s5h <- 6/50


s11 <- 3.95921531/50
s22 <- 4.98268949/50
s33 <- 3.9999999/50
s44 <- 5.00000000/50
s55 <- 6.0/50


mortality <- c(s11, s22, s33, s44, s55)
```

```{r}
source(here("working_model", "qb_stock_m.R"))

output <- qb_stock(species, tech, cost, baskets, mortality = mortality, years)

total_p <- colSums(output$profit_per_t, na.rm = TRUE)
profit_5 <- sum(total_p)

output$stock

last_stock <- tail(output$stock, 1)
qb1 <- as.data.frame(matrix(last_stock)) %>% 
  mutate(V1 = as.numeric(V1)) %>% 
  mutate(baskets = 1)

write_csv(qb1, here("working_model", "scratch", "end_biomass_5sp", "5_basket.csv"))
```



