---
title: "Intrinsic growth results"
author: "mauricio"
date: "2/27/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message=FALSE, warning=FALSE, echo=FALSE)

library(tidyverse)
library(here)
library(scales)
library(gridExtra)
library(grid)
library(kableExtra)
```

```{r}
# Read files results

# data
species_df <- read_csv(here("working_model","r explore","model run results files","species.csv"))
# data
tech_df <- read_csv(here("working_model","r explore","model run results files","tech_cost.csv"))

# general output files
output_sc1 <- read_csv(here("working_model","r explore","model run results files","output_b_r1.csv")) %>% 
  mutate(run = "Scenario 1",
         year = seq(0,30))
output_sc2 <- read_csv(here("working_model","r explore","model run results files","output_b_r2.csv"))%>% 
  mutate(run = "Scenario 2",
         year = seq(0,30))
output_sc3 <- read_csv(here("working_model","r explore","model run results files","output_b_r3.csv"))%>% 
  mutate(run = "Scenario 3",
         year = seq(0,30))

# sum of profits

npv_sc1 <- read_csv(here("working_model","r explore","model run results files","NPV_b_r1.csv")) %>% 
  mutate(run = "Scenario 1")
npv_sc2 <- read_csv(here("working_model","r explore","model run results files","NPV_b_r2.csv")) %>% 
  mutate(run = "Scenario 2")
npv_sc3 <- read_csv(here("working_model","r explore","model run results files","NPV_b_r3.csv")) %>% 
  mutate(run = "Scenario 3")

#Group them
all_outputs <- rbind(output_sc1, output_sc2, output_sc3) %>% 
  mutate(tot_profits = profit_per_t.t_1+profit_per_t.t_2+profit_per_t.t_3+profit_per_t.t_4+profit_per_t.t_5,
         tot_stock=stock.s_1+stock.s_2+stock.s_3+stock.s_4+stock.s_5)

NPVs <- rbind(npv_sc1, npv_sc2, npv_sc3) %>% 
  rename(total_profit=x)

```

# 1. Scenarios

In this section, we test how grouping stocks by their intrinsic growth (r) affect the profits, biomass and effort allocation. We are considering 3 species/fish have a low growth (r=0.1), and 2 species/fish with high growth (r = 0.4) at time zero. <br />

<br />
We considered 3 arrangement for the quota baskets:<br />
- *Species with similar r:* we have a QB of low r and a group of high r.<br />
- *The normal r species predominates in a basket:* we have a QB were the "low r" species predominates (2 low r and 1 high r), and the other basket has the remaining species (1 low r and 1 high r).<br />
- *The high r species predominates in a basket:*we have a QB were the "high r" species predominates (1 low r and 2 high r), and the other basket has the remaining species (2 low r).<br />

We are going to compare these arrangements in terms of biomass, efforts, ant total profits.
  
## 1.1 Parameters

```{r}

# Make tables
species_table <- kable(species_df, col.names = c("Species", "r", "K", "Starting stock (X)", "price")) %>% 
  kable_classic(full_width = F)

tech_table <- kable(tech_df, col.names = c("Tech", "
                                               q1", "q2", "q3", 
                                               "q4", "q5",
                                               "cost")) %>% 
  kable_classic(full_width = F)

species_table

tech_table
```


# 2. Biomass

## 2.1 Biomass per species

```{r}
# Graph
ggplot(data = all_outputs)+
  geom_line(aes(y=stock.s_1, x=year), color="blue")+ 
  geom_line(aes(y=stock.s_2, x=year), color="royalblue")+ 
  geom_line(aes(y=stock.s_3, x=year), color="lightblue")+ 
  geom_line(aes(y=stock.s_4, x=year), color="red")+ 
  geom_line(aes(y=stock.s_5, x=year), color="orange")+ 
  theme_minimal()+
  labs(x= "Years",
         y= "Stock Level (tons)")+
  facet_wrap(~ run, nrow=2)

```

```{r}
# Graph
stocck_1gr <- ggplot(data = all_outputs, aes(y=stock.s_1, x=year, group=run, color=run))+
  geom_line()+
  theme_minimal()+
  labs(x= "Years",
         y= "Stock 1 (tons)")

stocck_2gr <- ggplot(data = all_outputs, aes(y=stock.s_2, x=year, group=run, color=run))+
  geom_line()+
  theme_minimal()+
  labs(x= "Years",
         y= "Stock 2 (tons)")

stocck_3gr <- ggplot(data = all_outputs, aes(y=stock.s_3, x=year, group=run, color=run))+
  geom_line()+
  theme_minimal()+
  labs(x= "Years",
         y= "Stock 3 (tons)")

stocck_4gr <- ggplot(data = all_outputs, aes(y=stock.s_4, x=year, group=run, color=run))+
  geom_line()+
  theme_minimal()+
  labs(x= "Years",
         y= "Stock 4 (tons)")

stocck_5gr <- ggplot(data = all_outputs, aes(y=stock.s_5, x=year, group=run, color=run))+
  geom_line()+
  theme_minimal()+
  labs(x= "Years",
         y= "Stock 5 (tons)")

grid.arrange(stocck_1gr, stocck_4gr, stocck_2gr, stocck_5gr, stocck_3gr, ncol=2, nrow= 3)
```
<br />
- The low r species display a stable stock when they are part of quota baskets without high r species.<br />
- The high r species display a descending stock when they are part of quota baskets without low r species.<br />
- The high r species have a more stable stock over time in basket dominated by low r species, however the stocks of the low r species are diminishing over time.<br />

## 2.2 Total biomass in the ocean

```{r}
# Graph
ggplot(data = all_outputs, aes(y=tot_stock, x=year, group=run, color=run))+
  geom_line()+
  theme_minimal()+
  labs(x= "Years",
         y= "Stock (tons)")
  
```

<br />
- Despite the better results for high r species, scenario 2 provides the worst results in stock. <br />
- Grouping species with similar r seems more reasonable to enjoy stable stocks over time.<br />

# 3. Effort

```{r}
# Graph
ggplot(data = all_outputs)+
  geom_line(aes(y=effort.t_1, x=year), color="blue")+ 
  geom_line(aes(y=effort.t_2, x=year), color="royalblue")+ 
  geom_line(aes(y=effort.t_3, x=year), color="lightblue")+ 
  geom_line(aes(y=effort.t_4, x=year), color="red")+ 
  geom_line(aes(y=effort.t_5, x=year), color="orange")+ 
  theme_minimal()+
  labs(x= "Years",
         y= "Effort (units)")+
  facet_wrap(~ run, nrow=2)

```

```{r}
# Graph
e_1gr <- ggplot(data = all_outputs, aes(y=effort.t_1, x=year, group=run, color=run))+
  geom_line()+
  theme_minimal()+
  labs(x= "Years",
         y= "Tech 1")

e_2gr <- ggplot(data = all_outputs, aes(y=effort.t_2, x=year, group=run, color=run))+
  geom_line()+
  theme_minimal()+
  labs(x= "Years",
         y= "Tech 2")

e_3gr <- ggplot(data = all_outputs, aes(y=effort.t_3, x=year, group=run, color=run))+
  geom_line()+
  theme_minimal()+
  labs(x= "Years",
         y= "Tech 3")

e_4gr <- ggplot(data = all_outputs, aes(y=effort.t_4, x=year, group=run, color=run))+
  geom_line()+
  theme_minimal()+
  labs(x= "Years",
         y= "Tech 4")

e_5gr <- ggplot(data = all_outputs, aes(y=effort.t_5, x=year, group=run, color=run))+
  geom_line()+
  theme_minimal()+
  labs(x= "Years",
         y= "Tech 5")

grid.arrange(e_1gr, e_4gr, e_2gr, e_5gr, e_3gr, ncol=2, nrow= 3)
```

<br />
- In all the scenarios, the allocation favor the technologies that excel at harvesting high r species. The baskets dominated by high r species present **high mortality** (0.9). <br />
- Baskets with only low r species display low allocations (0 in many years) on the technologies that are good at catching them. <br />

# 4. Profit

# 4.1 Profit per technology
```{r}
# Graph
ggplot(data = all_outputs)+
  geom_line(aes(y=profit_per_t.t_1, x=year), color="blue")+ 
  geom_line(aes(y=profit_per_t.t_2, x=year), color="royalblue")+ 
  geom_line(aes(y=profit_per_t.t_3, x=year), color="lightblue")+ 
  geom_line(aes(y=profit_per_t.t_4, x=year), color="red")+ 
  geom_line(aes(y=profit_per_t.t_5, x=year), color="orange")+ 
  theme_minimal()+
  labs(x= "Years",
         y= "Profit (dollars)")+
  facet_wrap(~ run, nrow=2)

```

```{r}
# Graph
p_1gr <- ggplot(data = all_outputs, aes(y=profit_per_t.t_1, x=year, group=run, color=run))+
  geom_line()+
  theme_minimal()+
  labs(x= "Years",
         y= "Profit (tech 1)")

p_2gr <- ggplot(data = all_outputs, aes(y=profit_per_t.t_2, x=year, group=run, color=run))+
  geom_line()+
  theme_minimal()+
  labs(x= "Years",
         y= "Profit (tech 2)")

p_3gr <- ggplot(data = all_outputs, aes(y=profit_per_t.t_3, x=year, group=run, color=run))+
  geom_line()+
  theme_minimal()+
  labs(x= "Years",
         y= "Profit (tech 3)")

p_4gr <- ggplot(data = all_outputs, aes(y=profit_per_t.t_4, x=year, group=run, color=run))+
  geom_line()+
  theme_minimal()+
  labs(x= "Years",
         y= "Profit (tech 4)")

p_5gr <- ggplot(data = all_outputs, aes(y=profit_per_t.t_5, x=year, group=run, color=run))+
  geom_line()+
  theme_minimal()+
  labs(x= "Years",
         y= "Profit (tech 5)")

grid.arrange(p_1gr, p_4gr, p_2gr, p_5gr, p_3gr, ncol=2, nrow= 3)
```
<br />
- The low or zero efforts allocated in baskets with only low r species have null(or almost zero) profits in their best technologies. <br />
- Profits are positive for the technologies good at catching high r species in all scenarios. The best results are for baskets dominated by high r species. <br />

# 4.2 Total profit per scenario

```{r}
# Graph
ggplot(data = all_outputs, aes(y=tot_profits, x=year, group=run, color=run))+
  geom_line()+
  theme_minimal()+
  labs(x= "Years",
         y= "Profit (dollars)")

```

<br />
- Over time, the baskets dominated by high r species provide better total profits results in the period of analysis.

# 5. Summary

**Stocks**
<br />
- The low r species display a stable stock when they are part of quota baskets without high r species.<br />
- The high r species display a descending stock when they are part of quota baskets without low r species.<br />
- The high r species have a more stable stock over time in basket dominated by low r species, however the stocks of the low r species are diminishing over time.<br />
- Despite the better results for high r species, scenario 2 provides the worst results in stock. <br />
- Grouping species with similar r seems more reasonable to enjoy stable stocks over time.<br />

**Effort** 
<br />
- In all the scenarios, the allocation favor the technologies that excel at harvesting high r species. The baskets dominated by high r species present **high mortality** (0.9). <br />
- Baskets with only low r species display low allocations (0 in many years) on the technologies that are good at catching them. <br />

**Profit** 
<br />
- The low or zero efforts allocated in baskets with only low r species have null(or almost zero) profits in their best technologies. <br />
- Profits are positive for the technologies good at catching high r species in all scenarios. The best results are for baskets dominated by high r species. <br />
- Over time, the baskets dominated by high r species provide better total profits results in the period of analysis.



