---
title: "Health status results"
author: "mauricio"
date: "2/27/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message=FALSE, warning=FALSE, echo=FALSE)

library(tidyverse)
library(here)
library(scales)
library(gridExtra)
library(grid)
library(kableExtra)
```

```{r}
# Read files results

# data
species_df <- read_csv(here("working_model","health status explore","model run results files","species.csv"))
# data
tech_df <- read_csv(here("working_model","health status explore","model run results files","tech_cost.csv"))


# general output files
output_sc1 <- read_csv(here("working_model","health status explore","model run results files","output_b_overfish1.csv")) %>% 
  mutate(run = "Scenario 1",
         year = seq(0,30))
output_sc2 <- read_csv(here("working_model","health status explore","model run results files","output_b_overfish2.csv"))%>% 
  mutate(run = "Scenario 2",
         year = seq(0,30))
output_sc3 <- read_csv(here("working_model","health status explore","model run results files","output_b_overfish3.csv"))%>% 
  mutate(run = "Scenario 3",
         year = seq(0,30))

# sum of profits

npv_sc1 <- read_csv(here("working_model","health status explore","model run results files","NPV_b_overfish1.csv")) %>% 
  mutate(run = "Scenario 1")
npv_sc2 <- read_csv(here("working_model","health status explore","model run results files","NPV_b_overfish2.csv")) %>% 
  mutate(run = "Scenario 2")
npv_sc3 <- read_csv(here("working_model","health status explore","model run results files","NPV_b_overfish3.csv")) %>% 
  mutate(run = "Scenario 3")

#Group them
all_outputs <- rbind(output_sc1, output_sc2, output_sc3) %>% 
  mutate(tot_profits = profit_per_t.t_1+profit_per_t.t_2+profit_per_t.t_3+profit_per_t.t_4+profit_per_t.t_5,
         tot_stock=stock.s_1+stock.s_2+stock.s_3+stock.s_4+stock.s_5)

NPVs <- rbind(npv_sc1, npv_sc2, npv_sc3) %>% 
  rename(total_profit=x)

```

# 1. Scenarios

In this section, we test how grouping stocks by their initial stock affect the profits, biomass and effort allocation. We are considering 3 species/fish have a healthy stock (X_0 = 50), and 2 species/fish are overfished (X_0 = 15) at time zero. <br />

<br />
We considered 3 arrangement for the quota baskets:<br />
- *Species with similar health status:* we have a QB of healthy stocks and a group of overfished stocks.<br />
- *The healthy species predominates in a basket:* we have a QB were the healthy species predominates (2 healthy stocks and 1 overexploited stock), and the other basket has the remaining species (1 healthy stock and 1 overexploited stock).<br />
- *The overfished species predominates in a basket:*we have a QB were the overfished species predominates (1 healthy stock and 2 overexploited stocks), and the other basket has the remaining species (2 healthy stocks).
<br />

We are going to compare these arrangements in terms of biomass, efforts, ant total profits.  

## 1.1 Parameters

```{r}

# Make tables
species_table <- kable(species_df, col.names = c("Species", "r", "K", "Starting stock (X)", "price")) %>% 
  kable_classic(full_width = F)

tech_table <- kable(tech_df, col.names = c("Tech", "
                                               q1", "q2", "q3", 
                                               "q4", "q5",
                                               "cost")) %>% 
  kable_classic(full_width = F)

species_table

tech_table
```


# 2. Biomass

## 2.1 Biomass per species

```{r}
# Graph
ggplot(data = all_outputs)+
  geom_line(aes(y=stock.s_1, x=year), color="blue")+ 
  geom_line(aes(y=stock.s_2, x=year), color="royalblue")+ 
  geom_line(aes(y=stock.s_3, x=year), color="lightblue")+ 
  geom_line(aes(y=stock.s_4, x=year), color="red")+ 
  geom_line(aes(y=stock.s_5, x=year), color="orange")+ 
  theme_minimal()+
  labs(x= "Years",
         y= "Stock Level (tons)")+
  facet_wrap(~ run, nrow=2)

```

```{r}
# Graph
stocck_1gr <- ggplot(data = all_outputs, aes(y=stock.s_1, x=year, group=run, color=run))+
  geom_line()+
  theme_minimal()+
  labs(x= "Years",
         y= "Stock 1 (tons)")

stocck_2gr <- ggplot(data = all_outputs, aes(y=stock.s_2, x=year, group=run, color=run))+
  geom_line()+
  theme_minimal()+
  labs(x= "Years",
         y= "Stock 2 (tons)")

stocck_3gr <- ggplot(data = all_outputs, aes(y=stock.s_3, x=year, group=run, color=run))+
  geom_line()+
  theme_minimal()+
  labs(x= "Years",
         y= "Stock 3 (tons)")

stocck_4gr <- ggplot(data = all_outputs, aes(y=stock.s_4, x=year, group=run, color=run))+
  geom_line()+
  theme_minimal()+
  labs(x= "Years",
         y= "Stock 4 (tons)")

stocck_5gr <- ggplot(data = all_outputs, aes(y=stock.s_5, x=year, group=run, color=run))+
  geom_line()+
  theme_minimal()+
  labs(x= "Years",
         y= "Stock 5 (tons)")

grid.arrange(stocck_1gr, stocck_4gr, stocck_2gr, stocck_5gr, stocck_3gr, ncol=2, nrow= 3)
```
<br />
- Holding the rest of variables constant, the healthy stocks decline more in baskets dominated by healthy stocks. <br />
- Holding the rest of variables constant, the overfished stocks recover more in the baskets dominated by them. <br />

## 2.2 Total biomass in the ocean

```{r}
# Graph
ggplot(data = all_outputs, aes(y=tot_stock, x=year, group=run, color=run))+
  geom_line()+
  theme_minimal()+
  labs(x= "Years",
         y= "Stock (tons)")
  
```
<br />
Holding the other of parameters similar among species, the total stock declines during the first 5 years and recovers in the long term. Scenario 1 provides better stock results on the long term, but the trade off is putting additional pressure on the healthy stocks.<br />

# 3. Effort

```{r}
# Graph
ggplot(data = all_outputs)+
  geom_line(aes(y=effort.t_1, x=year), color="blue")+ 
  geom_line(aes(y=effort.t_2, x=year), color="royalblue")+ 
  geom_line(aes(y=effort.t_3, x=year), color="lightblue")+ 
  geom_line(aes(y=effort.t_4, x=year), color="red")+ 
  geom_line(aes(y=effort.t_5, x=year), color="orange")+ 
  theme_minimal()+
  labs(x= "Years",
         y= "Effort (units)")+
  facet_wrap(~ run, nrow=2)

```

```{r}
# Graph
e_1gr <- ggplot(data = all_outputs, aes(y=effort.t_1, x=year, group=run, color=run))+
  geom_line()+
  theme_minimal()+
  labs(x= "Years",
         y= "Tech 1")

e_2gr <- ggplot(data = all_outputs, aes(y=effort.t_2, x=year, group=run, color=run))+
  geom_line()+
  theme_minimal()+
  labs(x= "Years",
         y= "Tech 2")

e_3gr <- ggplot(data = all_outputs, aes(y=effort.t_3, x=year, group=run, color=run))+
  geom_line()+
  theme_minimal()+
  labs(x= "Years",
         y= "Tech 3")

e_4gr <- ggplot(data = all_outputs, aes(y=effort.t_4, x=year, group=run, color=run))+
  geom_line()+
  theme_minimal()+
  labs(x= "Years",
         y= "Tech 4")

e_5gr <- ggplot(data = all_outputs, aes(y=effort.t_5, x=year, group=run, color=run))+
  geom_line()+
  theme_minimal()+
  labs(x= "Years",
         y= "Tech 5")

grid.arrange(e_1gr, e_4gr, e_2gr, e_5gr, e_3gr, ncol=2, nrow= 3)
```
<br />
- Holding the other variables constant, we observe that baskets of similar elements display uniform effort units across all the period of analysis.<br />
- In the other scenarios, the effort favorable in harvesting overfished species increase while these species recover they stock. <br />

# 4. Profit

# 4.1 Profit per technology
```{r}
# Graph
ggplot(data = all_outputs)+
  geom_line(aes(y=profit_per_t.t_1, x=year), color="blue")+ 
  geom_line(aes(y=profit_per_t.t_2, x=year), color="royalblue")+ 
  geom_line(aes(y=profit_per_t.t_3, x=year), color="lightblue")+ 
  geom_line(aes(y=profit_per_t.t_4, x=year), color="red")+ 
  geom_line(aes(y=profit_per_t.t_5, x=year), color="orange")+ 
  theme_minimal()+
  labs(x= "Years",
         y= "Profit (dollars)")+
  facet_wrap(~ run, nrow=2)

```
```{r}
# Graph
p_1gr <- ggplot(data = all_outputs, aes(y=profit_per_t.t_1, x=year, group=run, color=run))+
  geom_line()+
  theme_minimal()+
  labs(x= "Years",
         y= "Profit (tech 1)")

p_2gr <- ggplot(data = all_outputs, aes(y=profit_per_t.t_2, x=year, group=run, color=run))+
  geom_line()+
  theme_minimal()+
  labs(x= "Years",
         y= "Profit (tech 2)")

p_3gr <- ggplot(data = all_outputs, aes(y=profit_per_t.t_3, x=year, group=run, color=run))+
  geom_line()+
  theme_minimal()+
  labs(x= "Years",
         y= "Profit (tech 3)")

p_4gr <- ggplot(data = all_outputs, aes(y=profit_per_t.t_4, x=year, group=run, color=run))+
  geom_line()+
  theme_minimal()+
  labs(x= "Years",
         y= "Profit (tech 4)")

p_5gr <- ggplot(data = all_outputs, aes(y=profit_per_t.t_5, x=year, group=run, color=run))+
  geom_line()+
  theme_minimal()+
  labs(x= "Years",
         y= "Profit (tech 5)")

grid.arrange(p_1gr, p_4gr, p_2gr, p_5gr, p_3gr, ncol=2, nrow= 3)
```
<br />
- Grouping healthy species (scenario 1) provide greater profits in their favorable technologies in all scenarios.<br />
- Grouping overfished species (scenario 1) provide less profits in their favorable technologies in all scenarios.<br />
- Grouping overfished species with healthy species, favor the increase of profits in tecnologies favorable for overfishe species.<br />

# 4.2 Total profit per scenario

```{r}
# Graph
ggplot(data = all_outputs, aes(y=tot_profits, x=year, group=run, color=run))+
  geom_line()+
  theme_minimal()+
  labs(x= "Years",
         y= "Profit (dollars)")

```
<br />

- Scenario 1 provides greater total profits in the short term.<br />

# 5. Summary

**Stocks**
<br />
- Holding the rest of variables constant, the healthy stocks decline more in baskets dominated by healthy stocks. <br />
- Holding the rest of variables constant, the overfished stocks recover more in the baskets dominated by them.<br /> 

**Effort** 
<br />
- Holding the other variables constant, we observe that baskets of similar elements display uniform effort units across all the period of analysis.<br />
- In the other scenarios, the effort favorable in harvesting overfished species increase while these species recover they stock. <br />

**Profit** 
<br />
- Grouping healthy species (scenario 1) provide greater profits in their favorable technologies in all scenarios.<br />
- Grouping overfished species (scenario 1) provide less profits in their favorable technologies in all scenarios.<br />
- Grouping overfished species with healthy species, favor the increase of profits in tecnologies favorable for overfishe species.<br />
- Scenario 1 provides greater total profits in the short term.

